---
title: "flat_full.Rmd for working package"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{=html}
<!-- 
Run this 'development' chunk

Store every call to library() that you need to run chunks line by line, as in a classical Rmd for analysis
-->
```
```{r development, include=FALSE}
library(testthat)
library(purrr)
library(RSelenium)
library(taskscheduleR)
```

```{=html}
<!--
# Description of your package

This will fill the description of your package.
Fill and run the content of this chunk, before anything else. 

Note: when you will use other flat templates, this part will be in a separate file. Do not be surprised!
-->
```
```{r description, eval=FALSE}
# Describe your package
fusen::fill_description(
  pkg = here::here(),
  fields = list(
    Title = "Breeding Tools",
    Description = "An R package that can automatically or periodically download data from the Nedap website in pig farm.",
    `Authors@R` = c(
      person("Guo Meng", email = "tony2015116@163.com", role = c("aut", "cre")),
      person(given = "Guo Meng", role = "cph")
    )
  ),
  overwrite=T
)
# Define License with use_*_license()
usethis::use_mit_license("Guo Meng")
#usethis::use_ccby_license()
```

# connect_to_browser

`connect_to_browser()` is used to start selenium webdriver service. You can use this function before using `download_csv_auto()` and `download_csv_schedule()`.

```{r function-connect_to_browser}
#' Start selenium webdriver service
#' 
#' @description
#'
#' `connect_to_browser()` is used to start the selenium webdriver service.
#' 
#' @param dest_dir The path of chrome browser dirver and selenium server.
#'
#' @return NULL
#' 
#' @importFrom wdauto "get_cd" "get_ss" "auto_cs"
#' @export
connect_to_browser <- function(dest_dir) {
  wdauto::get_cd(dest_dir)
  wdauto::get_ss(dest_dir)
  wdauto::auto_cs(dest_dir)
}
```

```{r examples-connect_to_browser}
connect_to_browser(dest_dir = "C:/Users/Dell/Desktop/test")
```

# download_csv_auto

`download_csv_auto()` can download pig performance test station CSVs from chrome browser.

```{=html}
<!-- 
This first section shows:

- the three parts necessary for a package: 'function', 'examples' and 'tests'.  
  + Note that the three following chunks have names accordingly.

-->
```
```{r function-download_csv_auto}
#' Automatically download CSVs
#' 
#' @description
#'
#' `download_csv_auto()` is used to download CSVs from chrome browser.
#' 
#' @param browser The browser you can use chrome or edge browser.
#' @param url The login url of pig performance test station website.
#' @param username The username of pig performance test station website.
#' @param password The password of pig performance test station website.
#' @param csv_position The pisiton of csv download item.
#' @param location Numeric value in string format.
#' @param data_date The dates of data download.
#' @param download_path The folder of downloading csv files.
#' @param save_path The folder you need to save renamed csv files.
#' @param ... other parameters.
#'
#' @return CSVs in the path of save_path.
#' 
#' @importFrom utils "capture.output"
#' @export

download_csv_auto <-
  function (browser,
            url,
            username,
            password,
            csv_position,
            location,
            data_date,
            download_path,
            save_path,
            ...) {
    # Argument checks
    if (!is.character(browser) || !(browser %in% c("chrome", "edge")))
  stop("The 'browser' parameter must be a character string, either 'chrome' or 'edge'.")
    if (!is.character(url))
      stop("url must be a character string.")
    if (!is.character(username))
      stop("username must be a character string.")
    if (!is.character(password))
      stop("password must be a character string.")
    if (!is.character(csv_position))
      stop("csv_position must be a character value.")
    if (!is.vector(location) ||
        !is.character(location))
      stop("location must be a character vector.")
    if (is.null(try(as.Date(data_date), silent = TRUE)
    ))
      stop("The 'data_date' parameter must be a valid date string.")
    if (!is.character(download_path))
      stop("download_path must be a character string.")
    if (!is.character(save_path))
      stop("save_path must be a character string.")
    
    # Define subdirectories
    subdir_have_data <- "have_data"
    subdir_no_data <- "no_data"
    
    # Create subdirectories with messages
    if (!dir.exists(file.path(save_path, subdir_have_data))) {
      dir.create(file.path(save_path, subdir_have_data), showWarnings = FALSE)
      message("Created directory: ", subdir_have_data)
    } else {
      message("Directory already exists: ", subdir_have_data)
    }
    
    if (!dir.exists(file.path(save_path, subdir_no_data))) {
      dir.create(file.path(save_path, subdir_no_data), showWarnings = FALSE)
      message("Created directory: ", subdir_no_data)
    } else {
      message("Directory already exists: ", subdir_no_data)
    }
    
    
    #浏览器参数设置
    get_browser_options <- function(browser, download_path_temp) {
    if (!browser %in% c("chrome", "edge")) {
      stop("Invalid browser specified. Use 'chrome' or 'edge'.")
    }
    
    if (browser == "chrome") {
      browser_options <- list(
        chromeOptions = list(
          prefs = list(
            "download.default_directory" = download_path_temp,
            "download.prompt_for_download" = FALSE,
            "download.directory_upgrade" = TRUE,
            "safebrowsing.enabled" = TRUE
          )
        )
      )
    } else if (browser == "edge") {
      browser <- "MicrosoftEdge"
      browser_options <- list(
        msedgeOptions = list(
          prefs = list(
            "download.default_directory" = download_path_temp,
            "download.prompt_for_download" = FALSE,
            "download.directory_upgrade" = TRUE,
            "safebrowsing.enabled" = TRUE
          )
        )
      )
    } #目前edge只能在edge默认的下载路径下载
    
    return(list(browserName = browser, options = browser_options))
  }
    #将download路径“/”转为“\\"
    download_path_temp = gsub("/", "\\\\", download_path)
    
    #选择浏览器获取不同浏览器参数
    browser_opts <- get_browser_options(browser, download_path_temp)
    
    
    remDr <- RSelenium::remoteDriver(
      browserName = browser_opts$browserName,
      extraCapabilities = browser_opts$options,
      remoteServerAddr = "127.0.0.1",
      port = 4444
    )
    
    
    suppress_print <- function() {
      remDr$open()
      remDr$navigate(url)
      login_user <- "//*[@id=\"frmLogin\"]/div[2]/input"
      login_passwd <- "//*[@id=\"frmLogin\"]/div[3]/input"
      login_user_ele <- remDr$findElement("xpath", login_user)
      login_passwd_ele <- remDr$findElement("xpath", login_passwd)
      user <- list(username)
      pass <- list(password)
      login_user_ele$sendKeysToElement(user)
      login_passwd_ele$sendKeysToElement(pass)
      login <- "//*[@id=\"login_button\"]"
      login_ele <- remDr$findElement("xpath", login)
      remDr$mouseMoveToLocation(webElement = login_ele)
      remDr$click()
    }
    
    capture.output(suppress_print()) #阻止打印
    
    Sys.sleep(sample(10, 1))
    
    iter_download <- function(station, data_date, ...) {
      choose_item <- "/html/body/div[1]/div[1]/ul/li[4]/a"
      choose_ele <- remDr$findElement("xpath", choose_item)
      remDr$mouseMoveToLocation(webElement = choose_ele)
      remDr$click()
      download_item <-
        paste0("//*[@id=\"reports_page\"]/div[2]/div/div[3]/ol/li[",
               {
                 {
                   csv_position
                 }
               },
               "]/a")
      download_ele <- remDr$findElement("xpath", download_item)
      remDr$mouseMoveToLocation(webElement = download_ele)
      remDr$click()
      location_start <-
        "//*[@id=\"criteria\"]/report-selection-range/div/div/div/div[1]/input"
      location_end <-
        "//*[@id=\"criteria\"]/report-selection-range/div/div/div/div[2]/input"
      location_ele_start <- remDr$findElement("xpath",
                                              location_start)
      location_ele_end <- remDr$findElement("xpath",
                                            location_end)
      location_ele_start$clearElement()
      location_ele_end$clearElement()
      location_start_num <- list(station, key = "enter")
      location_ele_start$sendKeysToElement(location_start_num)
      location_ele_end$clickElement()
      date_start <- "//*[@id=\"datetimepicker0\"]/input"
      date_end <- "//*[@id=\"datetimepicker1\"]/input"
      date_ele_start <- remDr$findElement("xpath", date_start)
      date_ele_end <- remDr$findElement("xpath", date_end)
      date_ele_start$clearElement()
      date_need_to_download <-
        stringr::str_replace_all(as.character(data_date),
                                 "-", ".")
      date_start_num <- list(date_need_to_download, key = "enter")
      date_end_num <- list(date_need_to_download, key = "enter")
      date_ele_start$sendKeysToElement(date_start_num)
      date_ele_end$clearElement()
      date_ele_end$sendKeysToElement(date_end_num)
      download_button <-
        "//*[@id=\"reports_download_csv_data\"]/div[4]/button"
      download_button_ele <- remDr$findElement("xpath",
                                               download_button)
      remDr$mouseMoveToLocation(webElement = download_button_ele)
      remDr$click()
      remDr$refresh()
    }
    
    Sys.sleep(3)
    
    # all_comb <- purrr::cross2(location, data_date) #注释的两行就可以完整的下载所有日期和所有测定站的csv数据
    # purrr::walk(all_comb, ~iter_download(.x[[1]], .x[[2]]), ...)
    
    all_station_oneday <-
      function(oneday_date, ...) {
        # Convert the integer date to a Date object and format it
        formatted_date <-
          format(as.Date(oneday_date, origin = "1970-01-01"), "%Y-%m-%d")
        
        cat("Downloading csv for date:", formatted_date, "\n")
        
        #为了方便修改csv名称包含数据日期，以某一天日期为参数，写函数all_station_oneday()下载该天所有测定站csv数据
        
        all_comb_station <-
          purrr::cross2(location, oneday_date) #组合所有测定站和单个日期
        purrr::walk(all_comb_station, ~ iter_download(.x[[1]], .x[[2]]), ...)#下载该日期所有csv数据
        
        
        rename_csv <- function(csv, ...) {
          #写函数rename_csv()来改变csv的名称
          csv_name <- tools::file_path_sans_ext(basename(csv))
          location_region <-
            stringr::str_extract(csv_name, "(?<=_)[:lower:]+\\d+-\\d+(?=_)")
          download_date <-
            stringr::str_extract(csv_name, "(?<=_)\\d+-\\d+-\\d+(?=_)")
          #download_date_trans <- stringr::str_replace_all(as.character(download_date), "-", ".")
          csv_new_name <-
            paste0(
              location_region,
              "_",
              oneday_date,
              "data",
              "_",
              download_date,
              "download",
              ".csv"
            )
          
          target_folder <-
            ifelse(file.size(csv) < 1024, "no_data", "have_data")
          destination_path <-
            file.path(save_path, target_folder, location_region)
          
          dir.create(destination_path, showWarnings = FALSE)
          
          file.rename(from = csv,
                      to = file.path(destination_path, csv_new_name))
        }
        
        down_list <-
          list.files(
            path = download_path,
            all.files = T,
            full.names = T,
            recursive = F,
            pattern = ".csv$"
          ) #下载的csv数据列表
        
        down_list_keep <-
          down_list[lubridate::as_date(file.info(down_list)$mtime) == lubridate::as_date(Sys.time())] #过滤csv文件，仅保留今日下载的csv
        purrr::walk(down_list_keep, rename_csv, ...) #批量改名
        
      }
    
    purrr::walk(data_date, all_station_oneday, .progress = T, ...) #循环每个日期下载csv
    
    remDr$quit() #退出浏览器
    
    return(invisible(NULL))
  }
```

```{=html}
<!--
Here is an example on how to use the function.
This should be a reproducible and working example
-->
```
```{r examples-download_csv_auto}
# Set parameters
stations = c("606","607")
data_date = c("2024-02-17","2024-02-18")
download_path = "C:/Users/Dell/Downloads/download_temp"
save_path = "C:/Users/Dell/Downloads/download_rename"
# Start selenium webdriver service
connect_to_browser(dest_dir = "C:/Users/Dell/Desktop/test")
# Download CSVs
download_csv_auto(browser = "chrome", 
                  url = Sys.getenv("web_url"), 
                  username = Sys.getenv("user_name"), 
                  password = Sys.getenv("user_password"),
                  csv_position = "1",
                  location = stations, 
                  data_date = data_date, 
                  download_path = download_path,
                  save_path = save_path)
```

# download_csv_schedule

`download_csv_schedule()` is used to make download task. You can download the *Yesterday* data at certain time in every day.

```{r function-download_csv_schedule}
#' Schedule automatic downloads of CSVs
#' 
#' @description
#'
#' `download_csv_schedule()` is used to make download task.
#' 
#' @param taskname A character string with the name of the task. Defaults to the filename. Should not contain any spaces.
#' @param schedule Either one of 'ONCE', 'MONTHLY', 'WEEKLY', 'DAILY', 'HOURLY', 'MINUTE', 'ONLOGON', 'ONIDLE.
#' @param starttime A time point in HH:mm format indicating when to run the script. Defaults to within 62 seconds.
#' @param startdate A date that specifies the first date on which to run the task. Only applicable if schedule is of type 'MONTHLY', 'WEEKLY', 'DAILY', 'HOURLY', 'MINUTE'. Defaults to today in '%d/%m/%Y' format. Change to your locale format if needed.
#' @param rscript_args Character string with further arguments passed on to Rscript.
#' @param ... other parameters.
#'
#' @return CSVs in the path of save_path.
#' @export

download_csv_schedule <- function(taskname, schedule, starttime, startdate, rscript_args = NULL, ...) {
  if (missing(taskname) || !is.character(taskname) || length(taskname) != 1) {
    stop("taskname must be a single character string")
  }

  if (missing(schedule) || !is.character(schedule) || length(schedule) != 1) {
    stop("schedule must be a single character string")
  }

  if (missing(starttime) || !is.character(starttime) || length(starttime) != 1) {
    stop("starttime must be a single character string")
  }

  if (missing(startdate) || !is.character(startdate) || length(startdate) != 1) {
    stop("startdate must be a single character string")
  }

  if (missing(rscript_args) || !is.list(rscript_args)) {
    stop("rscript_args must be a list of arguments")
  }

  # Save the function to a temporary script file with a shorter path
  short_temp_path <- "C:/Temp"
  dir.create(short_temp_path, showWarnings = FALSE)
  script_file <- file.path(short_temp_path, paste0(taskname, "_", sample(letters, 1), ".R"))

  my_function <- function(...) {
    pptsdd::download_csv_auto(data_date = Sys.Date()-1, ...)
  }

  # Save the arguments to a configuration file
  config_file <- file.path(short_temp_path, paste0("config_", taskname, ".txt"))
  cat("arg_list <- ", capture.output(dput(rscript_args)), file = config_file)

  write_function_to_script <- function(func, file_path, config_path) {
    func_name <- deparse(substitute(func))
    lines <- capture.output(dump(func_name, stdout()))
    lines <- c(lines, sprintf("source('%s')", config_path))
    lines <- c(lines, sprintf("do.call(%s, arg_list)", func_name))

    if (!file.exists(script_file)) {
      file.create(script_file)
    }

    con <- file(script_file, "w")
    on.exit(close(con), add = TRUE)
    writeLines(lines, con)
  }

  write_function_to_script(func = my_function, file_path = script_file, config_path = config_file)

  # Schedule the task
  taskscheduleR::taskscheduler_create(taskname = taskname,
                                      rscript = script_file, 
                                      schedule = schedule,
                                      starttime = starttime,
                                      startdate = startdate,
                                      rscript_args = NULL,
                                      ...)
}
```

```{r examples-download_csv_schedule}
# Make a download task
download_csv_schedule(taskname = "ppt_csv_download",
                      schedule = "DAILY",
                      starttime = "20:00",
                      startdate = format(Sys.Date(), "%Y/%m/%d"),
                      rscript_args = list(browser = "chrome", 
                                          url = Sys.getenv("web_url"),
                                          username = Sys.getenv("user_name"),
                                          password = Sys.getenv("user_password"),
                                          location = c("606","607"),
                                          csv_position = "1",
                                          download_path = "C:/Users/Dell/Downloads/download_temp",
                                          save_path = "C:/Users/Dell/Downloads/download_rename"))
# Delete download task
taskscheduleR::taskscheduler_delete("ppt_csv_download")
# Reset selenium webdriver service
disconnect_from_browser()
```

# disconnect_from_browser

`disconnect_from_browser()` is used to reset selenium webdriver service. You can use this function after using `download_csv_auto()` and `download_csv_schedule()`.

```{r function-connect_to_browser}
#' Reset selenium webdriver service
#' 
#' @description
#'
#' `disconnect_from_browser()` is used to reset selenium webdriver service.
#'
#' @return NULL
#' 
#' @importFrom wdauto "reset_cs"
#' @export

disconnect_from_browser <- function() {
  wdauto::reset_cs()
}
```

```{r examples-disconnect_from_browser}
disconnect_from_browser()
```

# get_csv

```{r function-get_csv}
#' Direct web scraping CSVs
#' 
#' @description
#' 
#' `get_csv()` allows you to directly download CSV files from the web. You can download CSV data for a specific location range or date range. 
#'
#' @param url A character string specifying the URL to log into.
#' @param username A character string specifying the username for login.
#' @param password A character string specifying the password for login.
#' @param location_min A character string specifying the minimum location.
#' @param location_max A character string specifying the maximum location.
#' @param date_min A Date object specifying the earliest date.
#' @param date_max A Date object specifying the latest date.
#' @param download_path A character string specifying the path where the downloaded CSV file should be saved.
#' @param show_message A logical value. If TRUE, a message will be displayed after the download. Default is FALSE.
#'
#' @return CSVs in the path of download_path.
#' 
#' @export

get_csv <- function(url, username, password, location_min, location_max, date_min, date_max, download_path, show_message = FALSE) {
  login_nedap(url, username, password) |>
    download_csv(location_min, location_max, date_min, date_max, download_path, show_message)
}

is_error_response <- function(resp) {
  httr2::resp_status(resp) >= 400
}

error_message_body <- function(resp) {
  paste("Error occurred with status code:", httr2::resp_status(resp))
}

login_nedap <- function(url, username, password) {
  # check if input parameters are missing
  if (missing(url) | missing(username) | missing(password)) {
    stop("Missing required input parameter(s).")
  }

  # check input parameters
  stopifnot(is.character(url), length(url) == 1)
  stopifnot(is.character(username), length(username) == 1)
  stopifnot(is.character(password), length(password) == 1)

  # create login request
  login_request <- httr2::request(paste0(url, "/login/LoginPage.web")) |>
    httr2::req_method("post") |>
    httr2::req_body_form(select_username = username, input_password = password) |>
    httr2::req_cookie_preserve(path = tempfile())

  # perform the request and get response
  login_response <- httr2::req_perform(login_request)

  # check if login is successful
  if (httr2::resp_status(login_response) != 200) {
    stop("Failed to login, please check your username or password.")
  }

  # get the login respond
  login_respond <- login_request |>
    httr2::req_retry(max_tries = 3, is_transient = \(resp) httr2::resp_status(resp) %in% c(429, 500, 503), backoff = ~10) |>
    httr2::req_error(is_error = is_error_response, body = error_message_body) |>
    httr2::req_url(paste0(url, "/pigperformancetesting/reports/DownloadCsvDataReport.web"))

  return(login_respond)
}

download_csv <- function(login_respond, location_min, location_max, date_min, date_max, download_path, show_message) {
  # check if input parameters are missing
  if (missing(login_respond) | missing(location_min) | missing(location_max) | missing(date_min) | missing(date_max) | missing(download_path)) {
    stop("Missing required input parameter(s).")
  }

  # check input parameters
  stopifnot(is.character(location_min), length(location_min) == 1)
  stopifnot(is.character(location_max), length(location_max) == 1)
  stopifnot(is.character(date_min), length(date_min) == 1)
  stopifnot(is.character(date_max), length(date_max) == 1)
  stopifnot(is.character(download_path), length(download_path) == 1)

  # create params
  params <- list(location_min = location_min, location_max = location_max, date_min = as.character(paste0(date_min, "T00:00:00Z")), date_max = as.character(paste0(date_max, "T00:00:00Z")))

  # perform the request and get response
  login_respond <- login_respond |>
    httr2::req_url_query(generate = "1", !!!params) |>
    httr2::req_perform()

  # check if the request is successful
  if (httr2::resp_status(login_respond) != 200) {
    stop("Failed to download csv, please check your parameters.")
  }

  # get the content and write to file
  content <- httr2::resp_body_string(login_respond)
  # check if location_min and location_max, date_min and date_max are the same
  location <- if(location_min == location_max) location_min else paste(location_min, location_max, sep="_")
  date <- if(date_min == date_max) date_min else paste(date_min, date_max, sep="_")
  filename <- paste0(location, "_location_", date, "_date_", Sys.Date(), "_download.csv")
  writeLines(content, file.path(download_path, filename))
  if (show_message) {
    cat(crayon::blue("\u25CF"), "Locations:", location, "and Dates:", date, "downloaded\n")
  }
}
```

```{r examples-get_csv}
# Download CSV data for a specific location range or date range.
get_csv(url = Sys.getenv("url"),
        username = Sys.getenv("username"),
        password = Sys.getenv("password"),
        location_min = "406",
        location_max = "407",
        date_min = "2024-02-18",
        date_max = "2024-02-19",
        download_path = "C:/Users/Dell/Downloads/download_rename", 
        show_message = TRUE)
```

# get_csv_auto

```{r function-get_csv_auto}
#' Direct web scraping CSVs
#' 
#' @description
#' 
#' `get_csv_auto` allows you to directly download CSV files from the web. You can download CSV data for a specific location or date.
#'
#' @param url A character string specifying the URL to log into.
#' @param username A character string specifying the username for login.
#' @param password A character string specifying the password for login.
#' @param location A character string specifying the location.
#' @param date A Date object specifying the date.
#' @param download_path A character string specifying the path where the downloaded CSV file should be saved.
#' @param show_message A logical value. If TRUE, a message will be displayed after the download. Default is FALSE.
#'
#' @return CSVs in the path of download_path.
#' 
#' @importFrom cli "pb_spin" "pb_current" "pb_total"
#' @export

get_csv_auto <- function(url, username, password, location, date, download_path, show_message = FALSE){
  login_request <- login_nedap(url, username, password)
  download_oneday_eachstation <- function(location, date) {
    download_csv(login_respond = login_request, location_min = location, location_max = location, date_min = date, date_max = date, download_path, show_message)
  }
  all_station_perday <- function(date) {
    # check if input parameter is missing
    if (missing(date)) {
      stop("Missing required input parameter: date.")
    }

    # check input parameter
    stopifnot(length(date) == 1)

    # Convert the integer date to a Date object and format it
    date <- format(as.Date(date), "%Y-%m-%d")

    # create a data frame with all combinations of location and date
    all_comb_station <- tidyr::expand_grid(location = location, date = date)

    cat(crayon::yellow("\u25CF"), "Downloading CSVs for date:", date, "\n")

    # download the csv file for each combination of location and date
    purrr::pwalk(all_comb_station, ~download_oneday_eachstation(location = ..1, date = ..2), .progress = F)

    #cat(crayon::yellow("\u25CF"), "Downloading CSVs for date:", date, "\n")
  }
  purrr::walk(date, all_station_perday, .progress = list(
    type = "iterator",
    format = "{cli::pb_spin} Downloading {cli::pb_current}/{cli::pb_total} dates",
    clear = TRUE))
  cat(crayon::green("\u25CF"), "All stations and dates nedap ppt CSVs had been downloaded.\n")

}
```

```{r examples-get_csv_auto}
# Download CSV data for a specific location or date
get_csv_auto(url = Sys.getenv("url"),
             username = Sys.getenv("username"),
             password = Sys.getenv("password"),
             location = c("607","608"),
             date = c("2024-02-18", "2024-02-19"),
             download_path = "C:/Users/Dell/Downloads/download_rename")
```

# get_csv_schedule

```{r function-get_csv_schedule}
#' Schedule automatic downloads of CSVs
#' 
#' @description
#'
#' `get_csv_schedule()` is used to make download task.
#' 
#' @param taskname A character string with the name of the task. Defaults to the filename. Should not contain any spaces.
#' @param schedule Either one of 'ONCE', 'MONTHLY', 'WEEKLY', 'DAILY', 'HOURLY', 'MINUTE', 'ONLOGON', 'ONIDLE.
#' @param starttime A time point in HH:mm format indicating when to run the script. Defaults to within 62 seconds
#' @param startdate A date that specifies the first date on which to run the task. Only applicable if schedule is of type 'MONTHLY', 'WEEKLY', 'DAILY', 'HOURLY', 'MINUTE'. Defaults to today in '%d/%m/%Y' format. Change to your locale format if needed.
#' @param rscript_args Character string with further arguments passed on to Rscript.
#' @param ... other parameters.
#'
#' @return CSV files in the path of save_path.
#' @export

get_csv_schedule <- function (taskname, schedule, starttime, startdate, rscript_args = NULL, ...) {
  if (missing(taskname) || !is.character(taskname) || length(taskname) !=
      1) {
    stop("taskname must be a single character string")
  }
  if (missing(schedule) || !is.character(schedule) || length(schedule) !=
      1) {
    stop("schedule must be a single character string")
  }
  if (missing(starttime) || !is.character(starttime) || length(starttime) !=
      1) {
    stop("starttime must be a single character string")
  }
  if (missing(startdate) || !is.character(startdate) || length(startdate) !=
      1) {
    stop("startdate must be a single character string")
  }
  if (missing(rscript_args) || !is.list(rscript_args)) {
    stop("rscript_args must be a list of arguments")
  }
  short_temp_path <- "C:/Temp"
  dir.create(short_temp_path, showWarnings = FALSE)
  script_file <- file.path(short_temp_path, paste0(taskname,
                                                   "_", sample(letters, 1), ".R"))
  my_function <- function(...) {
    pptsdd::get_csv_auto(date = Sys.Date() - 1,
                         ...)
  }
  config_file <- file.path(short_temp_path, paste0("config_",
                                                   taskname, ".txt"))
  cat("arg_list <- ", capture.output(dput(rscript_args)), file = config_file)
  write_function_to_script <- function(func, file_path, config_path) {
    func_name <- deparse(substitute(func))
    lines <- capture.output(dump(func_name, stdout()))
    lines <- c(lines, sprintf("source('%s')", config_path))
    lines <- c(lines, sprintf("do.call(%s, arg_list)", func_name))
    if (!file.exists(script_file)) {
      file.create(script_file)
    }
    con <- file(script_file, "w")
    on.exit(close(con), add = TRUE)
    writeLines(lines, con)
  }
  write_function_to_script(func = my_function, file_path = script_file,
                           config_path = config_file)
  taskscheduleR::taskscheduler_create(taskname = taskname,
                                      rscript = script_file, schedule = schedule, starttime = starttime,
                                      startdate = startdate, rscript_args = NULL, ...)
}
```

```{r examples-get_csv_schedule}
# Make a download task
get_csv_schedule(taskname = "ppt_csv_download",
                 schedule = "DAILY",
                 starttime = "20:00",
                 startdate = format(Sys.Date(), "%Y/%m/%d"),
                 rscript_args = list(browser = "chrome",
                                     url = Sys.getenv("url"),
                                     username = Sys.getenv("username"),
                                     password = Sys.getenv("password"),
                                     location = c("606","607"),
                                     download_path = "C:/Users/Dell/Downloads/download_rename"))
# Delete download task
taskscheduleR::taskscheduler_delete("ppt_csv_download")
# Reset selenium webdriver service
disconnect_from_browser()
```


That's it ! This the end of the documented story of our package. All components are there.

```{=html}
<!-- 
# Inflate your package

You're one inflate from paper to box.
Build your package from this very Rmd using `fusen::inflate()` 
-->
```
```{r development-inflate, eval=FALSE}
fusen::inflate(flat_file = "dev/csv_download.Rmd",
               check = T, vignette_name = "Basic Usage")

#fusen::load_flat_functions(flat_file = "dev/flat_full.Rmd")

```

```{=html}
<!-- 
- Verify your `"DESCRIPTION"` file has been updated
- Verify your function is in `"R/"` directory
- Verify your test is in `"tests/testthat/"` directory
- Verify this Rmd appears in `"vignettes/"` directory 
-->
```
