---
title: "flat_full.Rmd for working package"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{=html}
<!-- 
Run this 'development' chunk

Store every call to library() that you need to run chunks line by line, as in a classical Rmd for analysis
-->
```
```{r development, include=FALSE}
library(testthat)
library(purrr)
library(RSelenium)
library(taskscheduleR)
```

```{=html}
<!--
# Description of your package

This will fill the description of your package.
Fill and run the content of this chunk, before anything else. 

Note: when you will use other flat templates, this part will be in a separate file. Do not be surprised!
-->
```
```{r description, eval=FALSE}
# Describe your package
fusen::fill_description(
  pkg = here::here(),
  fields = list(
    Title = "Breeding Tools",
    Description = "An R package that can automatically or periodically download data from the Nedap website in pig farm.",
    `Authors@R` = c(
      person("Guo Meng", email = "tony2015116@163.com", role = c("aut", "cre")),
      person(given = "Guo Meng", role = "cph")
    )
  ),
  overwrite=T
)
# Define License with use_*_license()
usethis::use_mit_license("Guo Meng")
#usethis::use_ccby_license()
```

# connect_to_browser

This is the first function of our package. You can free up you hands and download pig performance test station data using function `download_csv_schedule()`.

```{r function-connect_to_browser}
#' setup chrome or edge broser dirver and selenium server
#' 
#' @description
#'
#' `connect_to_browser()` is deprecated. We will soon be totally
#' 
#' @param browser The browser you can choose chrome or edge, default is chrome
#' @param download_path The path of chrome or edge broser dirver and selenium server
#'
#' @return NULL
#' 
#' @importFrom utils "download.file" "tail" "unzip"
#' @export
connect_to_browser <- function(browser = "chrome", download_path) {
  # 参数检查
  if (!is.character(browser) || !browser %in% c("chrome", "edge")) {
    stop("Error: Invalid browser specified. Supported browsers are 'Chrome' or 'Microsoft Edge'.")
  }

  if (!is.character(download_path) || download_path == "") {
    stop("Error: 'download_path' argument must be a valid non-empty string.")
  }

  # 确保下载路径存在
  dir.create(download_path, showWarnings = FALSE)

  # 生成函数check_browsers_installed检查浏览器安装情况
  check_browsers_installed <- function(browser_name = NULL) {
    browsers <- list(
      list(
        name = "Chrome",
        reg_key = "HKEY_CURRENT_USER\\Software\\Google\\Chrome\\BLBeacon",
        version_var = "version"
      ),
      list(
        name = "Microsoft Edge",
        reg_key = "HKEY_CURRENT_USER\\Software\\Microsoft\\Edge\\BLBeacon",
        version_var = "version"
      )
    )

    if (!is.null(browser_name)) {
      browsers <- Filter(function(browser) browser$name == browser_name, browsers)
    }

    for (browser in browsers) {
      reg_query <- system(paste("reg query", shQuote(browser$reg_key), "/v", browser$version_var), intern = TRUE)

      if (length(reg_query) > 0) {
        browser_version <- regmatches(reg_query, regexpr("\\d+\\.\\d+\\.\\d+", reg_query))
        cat(browser$name, "is installed on this computer. Version:", browser_version, "\n")
      } else {
        cat("Error:", browser$name, "version not found.\n")
      }
    }
  }

  # 生成函数get_latest_release_chrome获取chrome驱动最新版本
  get_latest_release_chrome <- function(base_url, backup_url) {

    reg_query <- system("reg query \"HKEY_CURRENT_USER\\Software\\Google\\Chrome\\BLBeacon\" /v version", intern = TRUE)

    browser_version <- regmatches(reg_query, regexpr("\\d+\\.\\d+\\.\\d+", reg_query))
    browser_major_version <- regmatches(reg_query, regexpr("\\d+", reg_query))

    # 尝试从主要网址获取最新版本
    response <- tryCatch(httr::GET(paste0(base_url, "/LATEST_RELEASE_", browser_version)), error = function(e) NULL)

    # 如果主要网址失败，尝试从备份网址获取最新版本
    if (is.null(response) || httr::http_status(response)$category != "Success") {
      response <- httr::GET(paste0(backup_url, "/LATEST_RELEASE_", browser_version))
    }

    # 如果找不到完全匹配的驱动程序，尝试下载与浏览器主要版本号相同的最新驱动程序
    if (is.null(response) || httr::http_status(response)$category != "Success") {
      response <- tryCatch(httr::GET(paste0(base_url, "/LATEST_RELEASE_", browser_major_version)), error = function(e) NULL)
    }#使用closeset_version替代browser_major_version

    # 如果仍然无法获取版本信息，报错并退出
    if (is.null(response) || httr::http_status(response)$category != "Success") {
      cat("Error: Failed to download ChromeDriver from the provided URL. Please check the URL and try again.")
      return()
    }
    latest_release <- httr::content(response, as = "text", encoding = "UTF-8")
    # 获取计算机操作系统信息
    os <- tolower(Sys.info()[1])
    # 根据操作系统类型选择 Edge 驱动程序下载 URL
    if (os == "windows") {
      system_type <- Sys.info()["machine"]
      if (system_type == "x86-64") {
        download_url <- paste0(base_url, "/", latest_release, "/chromedriver_win32.zip")
      }
    } else if (os == "linux") {
      download_url <- paste0(base_url, "/", latest_release, "/chromedriver_linux64.zip")
    } else if (os == "darwin") {
      system_type <- Sys.info()["machine"]
      if (system_type == "arm64") {
        download_url <- paste0(base_url, "/", latest_release, "/chromedriver_mac_arm64.zip")
      } else if (system_type == "x86-64") {
        if (Sys.getenv("APPLE_SILICON_DEVICE") == "true") {
          download_url <- paste0(base_url, "/", latest_release, "/chromedriver_mac64.zip")
        }
      } else {
        # 不支持32位Mac系统
        stop("Unsupported system type: macOS 32-bit")
      }
    } else {
      # 不支持其他操作系统
      stop("Unsupported system type:", os)
    }
    return(download_url)
  }

  # 生成函数get_latest_release_edge获取edge驱动最新版本
  get_latest_release_edge <- function(base_url) {

    reg_query_edge <- system("reg query \"HKEY_CURRENT_USER\\Software\\Microsoft\\Edge\\BLBeacon\" /v version", intern = TRUE)

    edge_version <- regmatches(reg_query_edge, regexpr("\\d+\\.\\d+\\.\\d+", reg_query_edge))

    #page <- rvest::read_html(base_url)
    response <- httr::GET("https://msedgedriver.azureedge.net")
    html_content <- httr::content(response, as = "text", encoding = "UTF-8")

    # 解析页面内容，提取版本链接
    download_url <- rvest::read_html(html_content) |> rvest::html_nodes("url") |> rvest::html_text()
    # # Extract the table containing the version information
    # download_url <- rvest::html_nodes(page, "url") %>% html_text()
    # 构建 Edge 驱动下载 URL
    version_numbers <- sapply(download_url, function(x) gsub(".*/([0-9]+\\.[0-9]+\\.[0-9]+)\\.[0-9]+/.*", "\\1", x))
    #print(version_numbers)

    # 将版本号和浏览器版本转换为数值
    numeric_versions <- as.numeric(gsub("\\.", "", version_numbers))
    numeric_browser_version <- as.numeric(gsub("\\.", "", edge_version))

    # 提取大版本号
    major_versions <- as.integer(gsub("(\\d+)\\.\\d+\\.\\d+", "\\1", version_numbers))
    major_browser_version <- as.integer(gsub("(\\d+)\\.\\d+\\.\\d+", "\\1", edge_version))

    # 寻找小于等于浏览器版本的驱动程序版本，但不小于一个大版本
    compatible_versions <- version_numbers[(numeric_versions <= numeric_browser_version) & (major_versions >= major_browser_version - 1)]

    # 如果存在兼容版本，选择最接近的版本；否则返回错误或警告
    if (length(compatible_versions) > 0) {
      closest_version <- max(compatible_versions)
    } else {
      print("No compatible driver version found.")
    }
    # 找到“closest_version”的索引
    index <- which(compatible_versions == closest_version)

    # 获取该字符串的名称
    name <- names(compatible_versions)[index]

    # 获取计算机操作系统信息
    os <- tolower(Sys.info()[1])

    # 根据操作系统类型选择 Edge 驱动程序下载 URL
    if (os == "windows") {
      system_type <- Sys.info()["machine"]
      if (system_type == "x86-64") {
        selected_urls <- name[grepl(paste("win64", collapse = "|"), name)]
        edge_driver_download_url <- sample(selected_urls, 1)
      } else {
        selected_urls <- name[grepl(paste("win32", collapse = "|"), name)]
        edge_driver_download_url <- sample(selected_urls, 1)
      }
    } else if (os == "linux") {
      selected_urls <- name[grepl(paste("linux64", collapse = "|"), name)]
      edge_driver_download_url <- sample(selected_urls, 1)
    } else if (os == "darwin") {
      system_type <- Sys.info()["machine"]
      if (system_type == "arm64") {
        selected_urls <- name[grepl(paste("arm64", collapse = "|"), name)]
        edge_driver_download_url <- sample(selected_urls, 1)
      } else if (system_type == "x86-64") {
        if (Sys.getenv("APPLE_SILICON_DEVICE") == "true") {
          selected_urls <- name[grepl(paste("mac64_m1", collapse = "|"), name)]
          edge_driver_download_url <- sample(selected_urls, 1)
        } else {
          selected_urls <- name[grepl(paste("mac64", collapse = "|"), name)]
          edge_driver_download_url <- sample(selected_urls, 1)
        }
      } else {
        # 不支持32位Mac系统
        stop("Unsupported system type: macOS 32-bit")
      }
    } else {
      # 不支持其他操作系统
      stop("Unsupported system type:", os)
    }
  }

  # 生成函数get_latest_release_selenium获取最新版本的selenium
  get_latest_release_selenium <- function(selenium_base_url, selenium_backup_url) {
    versions_page <- tryCatch({
      rvest::read_html(selenium_base_url)
    }, error = function(e) {
      cat("Error: Failed to access the primary URL. Trying the backup URL...\n")
      rvest::read_html(selenium_backup_url)
    })

    latest_version <- versions_page |>
      rvest::html_nodes(xpath = "//key[contains(text(), 'selenium-server-standalone')]") |>
      rvest::html_text()
    latest_version_jar <- grep(".jar$", latest_version, value = T) |> tail(1)
    selenium_name <- gsub("^[0-9.]+/", "", latest_version_jar)
    selenium_file <- file.path(download_path, selenium_name)
    # 下载最新版本的selenium-server-standalone（如果selenium_file不存在）
    selenium_url <- paste0(selenium_base_url, latest_version_jar)
    backup_selenium_url <- paste0(selenium_backup_url, latest_version_jar)

    if (httr::http_status(httr::GET(selenium_url))$category == "Success") {
      return(selenium_url)
    } else if (httr::http_status(httr::GET(backup_selenium_url))$category == "Success") {
      return(backup_selenium_url)
    } else {
      stop("Both URLs are not available.")
    }
  }

  # 生成函数,下载文件的辅助函数
  download_with_error_handling <- function(url, file, ...) {
    tryCatch(
      {
        download.file(url, file, ...)
      },
      error = function(cond) {
        cat(paste0("An error occurred while downloading \n",
                   file, "\n"))
        message(cond)
      }
    )
  }

  # 下生成函数,载浏览器驱动并提取
  download_and_extract_driver <- function(browser, download_path, version_pattern, base_url, backup_url = NULL) {

    # 检查浏览器驱动文件是否存在
    browser_file <- file.path(download_path, version_pattern)

    # 如果浏览器驱动文件不存在，则执行以下操作
    if (!file.exists(browser_file)) {

      if (browser == "chrome") {
        latest_release_url <- get_latest_release_chrome(base_url, backup_url)
      } else if (browser == "edge") {
        latest_release_url <- get_latest_release_edge(base_url)
      } else {
        stop("Error: Unsupported browser. Please specify either 'chrome' or 'edge'.")
      }

      if (is.null(latest_release_url)) {
        stop(paste("Error: Failed to fetch the latest", browser, "driver release."))
      }

      # 截取 URL 中的文件名
      file_name <- basename(latest_release_url)

      # 拼接完整的下载文件路径
      download_file <- file.path(download_path, file_name)#paste0(download_path, "/", file_name)

      # 下载文件
      download_with_error_handling(latest_release_url, download_file, method = "curl")

      # 解压缩文件
      unzip(download_file, exdir = download_path)

      # 删除下载的压缩文件
      file.remove(download_file)
    }
  }


  # 生成函数download_selenium,下载selenium
  selenium_base_url <- "https://selenium-release.storage.googleapis.com/"
  selenium_backup_url <- "https://mirrors.huaweicloud.com/selenium/" # 请替换为您的备份网址
  download_selenium <- function(download_path, selenium_base_url, selenium_backup_url) {

    # 检查浏览器驱动文件是否存在
    existing_files <- list.files(download_path, pattern = ".jar$", full.names = TRUE)

    # 如果浏览器驱动文件不存在，则执行以下操作
    if (length(existing_files) == 0) {

      latest_release_url <- get_latest_release_selenium(selenium_base_url,selenium_backup_url) #获取最新版本selenium

      # 截取 URL 中的文件名
      file_name <- basename(latest_release_url)

      # 拼接完整的下载文件路径
      download_file <- file.path(download_path, file_name)#paste0(download_path, "/", file_name)

      # 下载文件
      download_with_error_handling(latest_release_url, download_file, method = "curl")
    }
  }

  # 生成selenium启动函数，启动selenium并生成开机启动的.bat文件
  start_selenium_server <- function(browser, download_path) {
    # Step 3: 启动Selenium服务器（如果尚未运行）
    task_list <- system2("wmic", args = c("process", "where", "name='java.exe'", "get", "ProcessId,CommandLine"), stdout = TRUE)
    # 使用 stri_encode 转换编码
    task_list <- stringi::stri_encode(task_list, from = "", to = "UTF-8")
    task_list_lines <- unlist(strsplit(task_list, split = "\r\n"))
    task_list_lines <- task_list_lines[grep("selenium-server-standalone", task_list_lines)]

    if (length(task_list_lines) > 0) {
      # 如果已有一个正在运行的 Selenium 服务器进程，等待它结束
      for (line in task_list_lines) {
        pid <- as.integer(gsub("^.*?([0-9]+).*$", "\\1", line))
        system2("taskkill", args = c("/F", "/PID", pid), stdout = FALSE, stderr = FALSE)
        cat(sprintf("Old selenium server process with PID %d terminated.\n", pid))
      }
      Sys.sleep(5) # 等待一段时间以确保进程已经结束
    }

    # 启动一个新的 Selenium 服务器进程
    startup_path <- file.path(Sys.getenv("APPDATA"), "Microsoft", "Windows", "Start Menu", "Programs", "Startup")
    startup_path <- gsub("\\\\", "/", startup_path)

    if (browser == "chrome") {
      browser_file <- file.path(download_path, "chromedriver.exe")# Chrome 驱动程序文件路径
      bat_file <- file.path(startup_path, "chrome_driver.bat")
    } else if (browser == "edge") {
      browser_file <- file.path(download_path, "msedgedriver.exe")# Edge 驱动程序文件路径
      bat_file <- file.path(startup_path, "edge_driver.bat")
    } else {
      stop("Invalid browser specified.")
    }

    selenium_file <- list.files(download_path, pattern = ".jar$", full.names = TRUE) # Selenium 服务器文件路径
    command <- sprintf("java -Dwebdriver.%s.driver=\"%s\" -jar \"%s\"", browser, browser_file, selenium_file)
    status <- system(command, wait = FALSE)
    if (status != 0) {
      cat("Error: Failed to start Selenium server.")
    } else {
      cat("New selenium server process created.")
    }
    # Step 4: 实现开机启动（如果.bat文件尚未创建）
    if (!file.exists(bat_file)) {

      bat_content <- paste(
        "@echo off",
        "cd /d %~dp0",
        "if \"%1\" == \"h\" goto begin",
        "mshta vbscript:createobject(\"wscript.shell\").run(\"%~nx0 h\",0)(window.close)&&exit",
        ":begin",
        command,
        sep = "\n")

      writeLines(bat_content, con = bat_file)
    }
  }

  if (browser == "chrome") {
    base_url <- "https://chromedriver.storage.googleapis.com"
    backup_url <- "https://mirrors.huaweicloud.com/chromedriver/"# 替换成实际的备份网址
    version_pattern <- "chromedriver.exe"
    browser = "chrome"
    browser_name = "Chrome" #仅用于check_browser_installed
    # 检查浏览器安装情况
    check_browsers_installed(browser_name)
    download_and_extract_driver(browser, download_path, version_pattern, base_url, backup_url)
    download_selenium(download_path, selenium_base_url, selenium_backup_url)
    start_selenium_server(browser, download_path)
  } else if (browser == "edge") {
    base_url <- "https://msedgedriver.azureedge.net/"
    version_pattern <- "msedgedriver.exe"
    browser = "edge"
    browser_name = "Microsoft Edge" #仅用于check_browser_installed
    # 检查浏览器安装情况
    check_browsers_installed(browser_name)
    download_and_extract_driver(browser, download_path, version_pattern, base_url)
    download_selenium(download_path, selenium_base_url, selenium_backup_url)
    start_selenium_server(browser, download_path)
  }
}
```

```{r examples-connect_to_browser}
connect_to_browser(browser = "chrome", download_path = "C:/Users/Dell/Downloads/selenium")
connect_to_browser(browser = "edge", download_path = "C:/Users/Dell/Downloads/selenium")
```

# download_csv_auto

This is the first function of our package. You can free up you hands and download pig performance test station data using function `download_csv_auto()`.

```{=html}
<!-- 
This first section shows:

- the three parts necessary for a package: 'function', 'examples' and 'tests'.  
  + Note that the three following chunks have names accordingly.

-->
```
```{r function-download_csv_auto}
#' Automatically download CSV
#' 
#' @description
#'
#' `download_csv_auto()` is deprecated. We will soon be totally
#' 
#' @param browser The browser you can chrome or edge
#' @param url The url of pig performance test station website
#' @param username The username of pig performance test station website
#' @param password The password of pig performance test station website
#' @param csv_position The pisiton of csv download item
#' @param location Numeric value in string format
#' @param data_date The dates of data download
#' @param download_path The folder of downloading csv files
#' @param save_path The folder you need to save renamed csv files
#' @param ... other parameters
#'
#' @return CSV files in the path of save_path
#' 
#' @importFrom utils "capture.output"
#' @export

download_csv_auto <-
  function (browser,
            url,
            username,
            password,
            csv_position,
            location,
            data_date,
            download_path,
            save_path,
            ...) {
    # Argument checks
    if (!is.character(browser) || !(browser %in% c("chrome", "edge")))
  stop("The 'browser' parameter must be a character string, either 'chrome' or 'edge'.")
    if (!is.character(url))
      stop("url must be a character string.")
    if (!is.character(username))
      stop("username must be a character string.")
    if (!is.character(password))
      stop("password must be a character string.")
    if (!is.character(csv_position))
      stop("csv_position must be a character value.")
    if (!is.vector(location) ||
        !is.character(location))
      stop("location must be a character vector.")
    if (is.null(try(as.Date(data_date), silent = TRUE)
    ))
      stop("The 'data_date' parameter must be a valid date string.")
    if (!is.character(download_path))
      stop("download_path must be a character string.")
    if (!is.character(save_path))
      stop("save_path must be a character string.")
    
    # Define subdirectories
    subdir_have_data <- "have_data"
    subdir_no_data <- "no_data"
    
    # Create subdirectories with messages
    if (!dir.exists(file.path(save_path, subdir_have_data))) {
      dir.create(file.path(save_path, subdir_have_data), showWarnings = FALSE)
      message("Created directory: ", subdir_have_data)
    } else {
      message("Directory already exists: ",
              file.path(save_path, subdir_have_data))
    }
    
    if (!dir.exists(file.path(save_path, subdir_no_data))) {
      dir.create(file.path(save_path, subdir_no_data), showWarnings = FALSE)
      message("Created directory: ", subdir_no_data)
    } else {
      message("Directory already exists: ",
              file.path(save_path, subdir_no_data))
    }
    
    
    #浏览器参数设置
    get_browser_options <- function(browser, download_path_temp) {
      if (!browser %in% c("chrome", "edge")) {
        stop("Invalid browser specified. Use 'chrome' or 'edge'.")
      }
      
      browser_options <- list(
        prefs = list(
          "download.default_directory" = download_path_temp,
          "download.prompt_for_download" = FALSE,
          "download.directory_upgrade" = TRUE,
          "safebrowsing.enabled" = TRUE
        )
      )
      
      if (browser == "edge") {
        browser = "MicrosoftEdge"
      }
      
      return(list(browserName = browser, options = browser_options))
    }
    #将download路径“/”转为“\\"
    download_path_temp = gsub("/", "\\\\", download_path)
    
    #选择浏览器获取不同浏览器参数
    browser_opts <- get_browser_options(browser, download_path_temp)
    
    
    remDr <- RSelenium::remoteDriver(
      browserName = browser_opts$browserName,
      extraCapabilities = browser_opts$options,
      remoteServerAddr = "127.0.0.1",
      port = 4444
    )
    
    
    suppress_print <- function() {
      remDr$open()
      remDr$navigate(url)
      login_user <- "//*[@id=\"frmLogin\"]/div[2]/input"
      login_passwd <- "//*[@id=\"frmLogin\"]/div[3]/input"
      login_user_ele <- remDr$findElement("xpath", login_user)
      login_passwd_ele <- remDr$findElement("xpath", login_passwd)
      user <- list(username)
      pass <- list(password)
      login_user_ele$sendKeysToElement(user)
      login_passwd_ele$sendKeysToElement(pass)
      login <- "//*[@id=\"login_button\"]"
      login_ele <- remDr$findElement("xpath", login)
      remDr$mouseMoveToLocation(webElement = login_ele)
      remDr$click()
    }
    
    capture.output(suppress_print()) #阻止打印
    
    Sys.sleep(sample(10, 1))
    
    iter_download <- function(station, data_date, ...) {
      choose_item <- "/html/body/div[1]/div[1]/ul/li[4]/a"
      choose_ele <- remDr$findElement("xpath", choose_item)
      remDr$mouseMoveToLocation(webElement = choose_ele)
      remDr$click()
      download_item <-
        paste0("//*[@id=\"reports_page\"]/div[2]/div/div[3]/ol/li[",
               {
                 {
                   csv_position
                 }
               },
               "]/a")
      download_ele <- remDr$findElement("xpath", download_item)
      remDr$mouseMoveToLocation(webElement = download_ele)
      remDr$click()
      location_start <-
        "//*[@id=\"criteria\"]/report-selection-range/div/div/div/div[1]/input"
      location_end <-
        "//*[@id=\"criteria\"]/report-selection-range/div/div/div/div[2]/input"
      location_ele_start <- remDr$findElement("xpath",
                                              location_start)
      location_ele_end <- remDr$findElement("xpath",
                                            location_end)
      location_ele_start$clearElement()
      location_ele_end$clearElement()
      location_start_num <- list(station, key = "enter")
      location_ele_start$sendKeysToElement(location_start_num)
      location_ele_end$clickElement()
      date_start <- "//*[@id=\"datetimepicker0\"]/input"
      date_end <- "//*[@id=\"datetimepicker1\"]/input"
      date_ele_start <- remDr$findElement("xpath", date_start)
      date_ele_end <- remDr$findElement("xpath", date_end)
      date_ele_start$clearElement()
      date_need_to_download <-
        stringr::str_replace_all(as.character(data_date),
                                 "-", ".")
      date_start_num <- list(date_need_to_download, key = "enter")
      date_end_num <- list(date_need_to_download, key = "enter")
      date_ele_start$sendKeysToElement(date_start_num)
      date_ele_end$clearElement()
      date_ele_end$sendKeysToElement(date_end_num)
      download_button <-
        "//*[@id=\"reports_download_csv_data\"]/div[4]/button"
      download_button_ele <- remDr$findElement("xpath",
                                               download_button)
      remDr$mouseMoveToLocation(webElement = download_button_ele)
      remDr$click()
      remDr$refresh()
    }
    
    Sys.sleep(3)
    
    # all_comb <- purrr::cross2(location, data_date) #注释的两行就可以完整的下载所有日期和所有测定站的csv数据
    # purrr::walk(all_comb, ~iter_download(.x[[1]], .x[[2]]), ...)
    
    all_station_oneday <-
      function(oneday_date, ...) {
        # Convert the integer date to a Date object and format it
        formatted_date <-
          format(as.Date(oneday_date, origin = "1970-01-01"), "%Y-%m-%d")
        
        cat("Downloading csv for date:", formatted_date, "\n")
        
        #为了方便修改csv名称包含数据日期，以某一天日期为参数，写函数all_station_oneday()下载该天所有测定站csv数据
        
        all_comb_station <-
          purrr::cross2(location, oneday_date) #组合所有测定站和单个日期
        purrr::walk(all_comb_station, ~ iter_download(.x[[1]], .x[[2]]), ...)#下载该日期所有csv数据
        
        
        rename_csv <- function(csv, ...) {
          #写函数rename_csv()来改变csv的名称
          csv_name <- tools::file_path_sans_ext(basename(csv))
          location_region <-
            stringr::str_extract(csv_name, "(?<=_)[:lower:]+\\d+-\\d+(?=_)")
          download_date <-
            stringr::str_extract(csv_name, "(?<=_)\\d+-\\d+-\\d+(?=_)")
          #download_date_trans <- stringr::str_replace_all(as.character(download_date), "-", ".")
          csv_new_name <-
            paste0(
              location_region,
              "_",
              oneday_date,
              "data",
              "_",
              download_date,
              "download",
              ".csv"
            )
          
          target_folder <-
            ifelse(file.size(csv) < 1024, "no_data", "have_data")
          destination_path <-
            file.path(save_path, target_folder, location_region)
          
          dir.create(destination_path, showWarnings = FALSE)
          
          file.rename(from = csv,
                      to = file.path(destination_path, csv_new_name))
        }
        
        down_list <-
          list.files(
            path = download_path,
            all.files = T,
            full.names = T,
            recursive = F,
            pattern = ".csv$"
          ) #下载的csv数据列表
        
        down_list_keep <-
          down_list[lubridate::as_date(file.info(down_list)$mtime) == lubridate::as_date(Sys.time())] #过滤csv文件，仅保留今日下载的csv
        purrr::walk(down_list_keep, rename_csv, ...) #批量改名
        
      }
    
    purrr::walk(data_date, all_station_oneday, .progress = T, ...) #循环每个日期下载csv
    
    remDr$quit() #退出浏览器
    
    return(invisible(NULL))
  }
```

```{=html}
<!--
Here is an example on how to use the function.
This should be a reproducible and working example
-->
```
```{r examples-download_csv_auto}
stations = c("1801","1802")
data_date = c("2023-03-29","2023-03-30")
download_path = "C:/Users/Dell/Downloads"
save_path = "C:/Users/Dell/Downloads/test"

download_csv_auto(browser = "edge", 
                  url = Sys.getenv("web_url"), 
                  username = Sys.getenv("user_name"), 
                  password = Sys.getenv("user_password"),
                  csv_position = "1",
                  location = stations, 
                  data_date = data_date, 
                  download_path = download_path,
                  save_path = save_path)
```

# download_csv_schedule

This is the first function of our package. You can free up you hands and download pig performance test station data using function `download_csv_schedule()`.

```{r function-download_csv_schedule}
#' Schedule automatic downloads of CSV
#' 
#' @description
#'
#' `download_csv_schedule()` is deprecated. We will soon be totally
#' 
#' @param taskname A character string with the name of the task. Defaults to the filename. Should not contain any spaces
#' @param schedule Either one of 'ONCE', 'MONTHLY', 'WEEKLY', 'DAILY', 'HOURLY', 'MINUTE', 'ONLOGON', 'ONIDLE
#' @param starttime A timepoint in HH:mm format indicating when to run the script. Defaults to within 62 seconds
#' @param startdate A date that specifies the first date on which to run the task. Only applicable if schedule is of type 'MONTHLY', 'WEEKLY', 'DAILY', 'HOURLY', 'MINUTE'. Defaults to today in '%d/%m/%Y' format. Change to your locale format if needed
#' @param rscript_args Character string with further arguments passed on to Rscript
#' @param ... other parameters
#'
#' @return CSV files in the path of save_path
#' @export

download_csv_schedule <- function(taskname, schedule, starttime, startdate, rscript_args = NULL, ...) {
  if (missing(taskname) || !is.character(taskname) || length(taskname) != 1) {
    stop("taskname must be a single character string")
  }

  if (missing(schedule) || !is.character(schedule) || length(schedule) != 1) {
    stop("schedule must be a single character string")
  }

  if (missing(starttime) || !is.character(starttime) || length(starttime) != 1) {
    stop("starttime must be a single character string")
  }

  if (missing(startdate) || !is.character(startdate) || length(startdate) != 1) {
    stop("startdate must be a single character string")
  }

  if (missing(rscript_args) || !is.list(rscript_args)) {
    stop("rscript_args must be a list of arguments")
  }

  # Save the function to a temporary script file with a shorter path
  short_temp_path <- "C:/Temp"
  dir.create(short_temp_path, showWarnings = FALSE)
  script_file <- file.path(short_temp_path, paste0(taskname, "_", sample(letters, 1), ".R"))

  my_function <- function(...) {
    pptsdd::download_csv_auto(data_date = Sys.Date()-1, ...)
  }

  # Save the arguments to a configuration file
  config_file <- file.path(short_temp_path, paste0("config_", taskname, ".txt"))
  cat("arg_list <- ", capture.output(dput(rscript_args)), file = config_file)

  write_function_to_script <- function(func, file_path, config_path) {
    func_name <- deparse(substitute(func))
    lines <- capture.output(dump(func_name, stdout()))
    lines <- c(lines, sprintf("source('%s')", config_path))
    lines <- c(lines, sprintf("do.call(%s, arg_list)", func_name))

    if (!file.exists(script_file)) {
      file.create(script_file)
    }

    con <- file(script_file, "w")
    on.exit(close(con), add = TRUE)
    writeLines(lines, con)
  }

  write_function_to_script(func = my_function, file_path = script_file, config_path = config_file)

  # Schedule the task
  taskscheduleR::taskscheduler_create(taskname = taskname,
                                      rscript = script_file, 
                                      schedule = schedule,
                                      starttime = starttime,
                                      startdate = startdate,
                                      rscript_args = NULL,
                                      ...)
}
```

```{r examples-download_csv_schedule}
download_csv_schedule(taskname = "ppt_csv_download",
                      schedule = "DAILY",
                      starttime = "20:05",
                      startdate = format(Sys.Date(), "%Y/%m/%d"),
                      rscript_args = list(browser = "edge", 
                                          url = Sys.getenv("web_url"),
                                          username = Sys.getenv("user_name"),
                                          password = Sys.getenv("user_password"),
                                          location = c("1801","1802"),
                                          csv_position = "1",
                                          download_path = "C:/Users/Dell/Downloads",
                                          save_path = "C:/Users/Dell/Downloads/test"))
```

# disconnect_from_browser

```{r function-connect_to_browser}
#' stop chrome or edge broser dirver and selenium server
#' 
#' @description
#'
#' `disconnect_from_browser()` is deprecated. We will soon be totally
#' 
#'
#' @return NULL
#' 
#' @export

disconnect_from_browser <- function() {

  # Step 1: 关闭Selenium服务器
  task_list <- system2("wmic", args = c("process", "where", "name='java.exe'", "get", "ProcessId,CommandLine"), stdout = TRUE)
  # 使用 stri_encode 转换编码
  task_list <- stringi::stri_encode(task_list, from = "", to = "UTF-8")
  task_list_lines <- unlist(strsplit(task_list, split = "\r\n"))
  task_list_lines <- task_list_lines[grep("selenium-server-standalone", task_list_lines)]

  if (length(task_list_lines) > 0) {
    for (line in task_list_lines) {
      pid <- as.integer(gsub("^.*?([0-9]+).*$", "\\1", line))
      system2("taskkill", args = c("/F", "/PID", pid), stdout = FALSE, stderr = FALSE)
      cat(sprintf("Selenium server process with PID %d terminated.\n", pid))
    }
  } else {
    cat("No Selenium server process found.\n")
  }

  # Step 2: 关闭所有正在运行的chromedriver.exe进程
  chromedriver_list <- system2("wmic", args = c("process", "where", "name='chromedriver.exe'", "get", "ProcessId,CommandLine"), stdout = TRUE)
  # 使用 stri_encode 转换编码
  chromedriver_list <- stringi::stri_encode(chromedriver_list, from = "", to = "UTF-8")
  chromedriver_list_lines <- unlist(strsplit(chromedriver_list, split = "\r\n"))
  chromedriver_list_lines <- chromedriver_list_lines[grep("chromedriver.exe", chromedriver_list_lines)]

  if (length(chromedriver_list_lines) > 0) {
    for (line in chromedriver_list_lines) {
      pid <- as.integer(gsub("^.*?([0-9]+).*$", "\\1", line))
      system2("taskkill", args = c("/F", "/PID", pid), stdout = FALSE, stderr = FALSE)
      cat(sprintf("Chromedriver process with PID %d terminated.\n", pid))
    }
  } else {
    cat("No Chromedriver process found.\n")
  }

  # 关闭所有正在运行的 msedgedriver.exe 进程
  msedgedriver_list <- system2("wmic", args = c("process", "where", "name='msedgedriver.exe'", "get", "ProcessId,CommandLine"), stdout = TRUE)
  # 使用 stri_encode 转换编码
  msedgedriver_list <- stringi::stri_encode(msedgedriver_list, from = "", to = "UTF-8")
  msedgedriver_list_lines <- unlist(strsplit(msedgedriver_list, split = "\r\n"))
  msedgedriver_list_lines <- msedgedriver_list_lines[grep("msedgedriver.exe", msedgedriver_list_lines)]

  if (length(msedgedriver_list_lines) > 0) {
    for (line in msedgedriver_list_lines) {
      pid <- as.integer(gsub("^.*?([0-9]+).*$", "\\1", line))
      system2("taskkill", args = c("/F", "/PID", pid), stdout = FALSE, stderr = FALSE)
      cat(sprintf("Microsoft Edge driver process with PID %d terminated.\n", pid))
    }
  } else {
    cat("No Msedgedriver process found.\n")
  }

  # Step 2: 取消开机启动
  startup_path <- file.path(Sys.getenv("APPDATA"), "Microsoft", "Windows", "Start Menu", "Programs", "Startup")
  startup_path <- gsub("\\\\", "/", startup_path)
  #bat_file <- file.path(startup_path, "chrome_driver.bat")
  bat_file <- list.files(startup_path, ".bat$", full.names = T)

  if (length(bat_file) > 0) {
    file.remove(bat_file)
    cat("Startup .bat file removed.\n")
  } else {
    cat("No startup .bat file found.\n")
  }
}
```

```{r examples-disconnect_from_browser}
disconnect_from_browser()
```

That's it ! This the end of the documented story of our package. All components are there.

```{=html}
<!-- 
# Inflate your package

You're one inflate from paper to box.
Build your package from this very Rmd using `fusen::inflate()` 
-->
```
```{r development-inflate, eval=FALSE}
fusen::inflate(flat_file = "dev/csv_download.Rmd",
               check = T, vignette_name = "Basic Usage")

#fusen::load_flat_functions(flat_file = "dev/flat_full.Rmd")

```

```{=html}
<!-- 
- Verify your `"DESCRIPTION"` file has been updated
- Verify your function is in `"R/"` directory
- Verify your test is in `"tests/testthat/"` directory
- Verify this Rmd appears in `"vignettes/"` directory 
-->
```
