---
title: "flat_full.Rmd for working package"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{=html}
<!-- 
Run this 'development' chunk

Store every call to library() that you need to run chunks line by line, as in a classical Rmd for analysis
-->
```
```{r development, include=FALSE}
library(testthat)
library(purrr)
library(RSelenium)
library(taskscheduleR)
```

```{=html}
<!--
# Description of your package

This will fill the description of your package.
Fill and run the content of this chunk, before anything else. 

Note: when you will use other flat templates, this part will be in a separate file. Do not be surprised!
-->
```
```{r description, eval=FALSE}
# Describe your package
fusen::fill_description(
  pkg = here::here(),
  fields = list(
    Title = "Breeding Tools",
    Description = "An R package that can automatically or periodically download data from the Nedap website in pig farm.",
    `Authors@R` = c(
      person("Guo Meng", email = "tony2015116@163.com", role = c("aut", "cre")),
      person(given = "Guo Meng", role = "cph")
    )
  ),
  overwrite=T
)
# Define License with use_*_license()
usethis::use_mit_license("Guo Meng")
#usethis::use_ccby_license()
```

# connect_to_browser

`connect_to_browser()` is used to start selenium webdriver service. You can use this function before using `download_csv_auto()` and `download_csv_schedule()`.

```{r function-connect_to_browser}
#' Start selenium webdriver service
#' 
#' @description
#'
#' `connect_to_browser()` is used to start the selenium webdriver service.
#' 
#' @param dest_dir The path of chrome browser dirver and selenium server.
#'
#' @return NULL
#' 
#' @importFrom wdauto "get_cd" "get_ss" "auto_cs"
#' @export
connect_to_browser <- function(dest_dir) {
  wdauto::get_cd(dest_dir)
  wdauto::get_ss(dest_dir)
  wdauto::auto_cs(dest_dir)
}
```

```{r examples-connect_to_browser}
connect_to_browser(dest_dir = "C:/Users/Dell/Desktop/test")
```

# download_csv_auto

`download_csv_auto()` can download pig performance test station CSVs from chrome browser.

```{=html}
<!-- 
This first section shows:

- the three parts necessary for a package: 'function', 'examples' and 'tests'.  
  + Note that the three following chunks have names accordingly.

-->
```
```{r function-download_csv_auto}
#' Automatically download CSVs
#' 
#' @description
#'
#' `download_csv_auto()` is used to download CSVs from chrome browser.
#' 
#' @param url The login url of pig performance test station website.
#' @param username The username of pig performance test station website.
#' @param password The password of pig performance test station website.
#' @param csv_position The pisiton of csv download item.
#' @param location Numeric value in string format.
#' @param date The dates of data download.
#' @param download_path The folder of downloading csv files.
#'
#' @return CSVs in the path of save_path.
#' 
#' @importFrom utils "capture.output"
#' @export

download_csv_auto <- function(url, username, password, csv_position, location, date, download_path) {
  # Argument checks
  if (!is.character(url))
    stop("url must be a character string.")
  if (!is.character(username))
    stop("username must be a character string.")
  if (!is.character(password))
    stop("password must be a character string.")
  if (!is.character(csv_position))
    stop("csv_position must be a character value.")
  if (!is.vector(location) ||
      !is.character(location))
    stop("location must be a character vector.")
  if (is.null(try(as.Date(date), silent = TRUE)
  ))
    stop("The 'date' parameter must be a valid date string.")
  if (!is.character(download_path))
    stop("download_path must be a character string.")

  # Function to check and create subdirectories
  checkAndCreateSubdirs(download_path)
  # Login url
  url <- paste0(url, "/login/LoginPage.web")
  # Function to get browser options for chrome
  browser_opts <- get_browser_options(browser = "chrome", download_path)

  remDr <- RSelenium::remoteDriver(
    browserName = browser_opts$browserName,
    extraCapabilities = browser_opts$options,
    remoteServerAddr = "127.0.0.1",
    port = 4444
  )
  # Function to login to a website using Selenium
  capture.output(login_to_website(remDr, url, username, password)) #阻止打印

  Sys.sleep(sample(10, 1))

  # Define a function that downloads data for a specified station and date
  iter_download <- function(location, date) {
    # Define the XPath for the item to choose
    choose_item <- "/html/body/div[1]/div[1]/ul/li[4]/a"


    # Find the element and click on it
    choose_ele <- remDr$findElement("xpath", choose_item)
    remDr$mouseMoveToLocation(webElement = choose_ele)
    remDr$click()


    # Define the XPath for the download item
    download_item <- paste0("//*[@id=\"reports_page\"]/div[2]/div/div[3]/ol/li[",csv_position,"]/a")


    # Find the download element and click on it
    download_ele <- remDr$findElement("xpath", download_item)
    remDr$mouseMoveToLocation(webElement = download_ele)
    remDr$click()


    # Define the XPaths for the start and end locations
    location_start <- "//*[@id=\"criteria\"]/report-selection-range/div/div/div/div[1]/input"
    location_end <- "//*[@id=\"criteria\"]/report-selection-range/div/div/div/div[2]/input"


    # Find the elements for the start and end locations
    location_ele_start <- remDr$findElement("xpath", location_start)
    location_ele_end <- remDr$findElement("xpath", location_end)


    # Clear the elements
    location_ele_start$clearElement()
    location_ele_end$clearElement()


    # Define the start location number
    location_start_num <- list(location, key = "enter")


    # Send the start location number
    location_ele_start$sendKeysToElement(location_start_num)


    # Click on the end location element
    location_ele_end$clickElement()


    # Define the XPaths for the start and end dates
    date_start <- "//*[@id=\"datetimepicker0\"]/input"
    date_end <- "//*[@id=\"datetimepicker1\"]/input"


    # Find the elements for the start and end dates
    date_ele_start <- remDr$findElement("xpath", date_start)
    date_ele_end <- remDr$findElement("xpath", date_end)


    # Clear the elements
    date_ele_start$clearElement()


    # Replace "-" with "." in the date
    date_need_to_download <- stringr::str_replace_all(as.character(date), "-", ".")


    # Define the start and end date numbers
    date_start_num <- list(date_need_to_download, key = "enter")
    date_end_num <- list(date_need_to_download, key = "enter")


    # Send the start and end date numbers
    date_ele_start$sendKeysToElement(date_start_num)
    date_ele_end$clearElement()
    date_ele_end$sendKeysToElement(date_end_num)


    # Define the XPath for the download button
    download_button <- "//*[@id=\"reports_download_csv_data\"]/div[4]/button"


    # Find the download button element and click on it
    download_button_ele <- remDr$findElement("xpath", download_button)
    remDr$mouseMoveToLocation(webElement = download_button_ele)
    remDr$click()


    # Refresh the page
    remDr$refresh()
  }

  #下面的函数中rename待修改
  all_station_oneday <- function(date) {
    # Convert the integer date to a Date object and format it
    date <- format(as.Date(date), "%Y-%m-%d")

    cat(crayon::yellow("\u25CF"), "Downloading CSVs for date:", date, "\n")

    # create a data frame with all combinations of location and date
    all_comb_station <- tidyr::expand_grid(location = location, date = date)

    # download the csv file for each combination of location and date
    purrr::pwalk(all_comb_station, ~iter_download(location = ..1, date = ..2), .progress = F)

    # Function to rename a csv file
    rename_csv <- function(csv) {
      # Extract the name of the csv file without the extension
      csv_name <- tools::file_path_sans_ext(basename(csv))

      # Extract location and region from the csv_name using a regex pattern
      location <- stringr::str_extract(csv_name, "(?<=location)\\d+")
      # Extract download date from the csv_name using a regex pattern
      download_date <- stringr::str_extract(csv_name, "(?<=_)\\d+-\\d+-\\d+(?=_)")

      # Construct the new name for the csv file
      csv_new_name <- paste0("location", location, "_", date, "data_", download_date, "download", ".csv")

      # Determine the target folder based on the file size
      target_folder <- ifelse(file.size(csv) < 1024, "EmptyCSVs", "NonEmptyCSVs")

      # Construct the destination path
      destination_path <- file.path(download_path, target_folder, location)

      # Create the destination directory if it does not exist
      dir.create(destination_path, showWarnings = FALSE)

      # Rename the file
      file.rename(from = csv, to = file.path(destination_path, csv_new_name))
    }

    # Get a list of all csv files in the download directory
    down_list <- list.files(path = download_path, all.files = T, full.names = T, recursive = F, pattern = ".csv$")

    # Filter the list to keep only the files that were downloaded today
    down_list_keep <- down_list[lubridate::as_date(file.info(down_list)$mtime) == lubridate::as_date(Sys.time())]

    # Apply the rename_csv function to each file in the filtered list
    purrr::walk(down_list_keep, rename_csv)
  }

  purrr::walk(date, all_station_oneday, .progress = FALSE)
  cat(crayon::green("\u25CF"), "All stations and dates nedap ppt CSVs had been downloaded.\n")

  remDr$quit() #退出浏览器

  return(invisible(NULL))
}

# Function to check and create subdirectories
checkAndCreateSubdirs <- function(download_path) {
  # Define subdirectories
  subdirs <- c("NonEmptyCSVs", "EmptyCSVs")

  # Check and create subdirectories
  for (subdir in subdirs) {
    dir_path <- file.path(download_path, subdir)
    if (!dir.exists(dir_path)) {
      dir.create(dir_path, showWarnings = FALSE)
      cat(crayon::blue("\u25CF"), "Created directory:", subdir, "\n")
    } else {
      cat(crayon::green("\u25CF"), "Directory already exists:", subdir, "\n")
    }
  }
}

# Function to get browser options for chrome
get_browser_options <- function(browser = "chrome", download_path) {
  # Check if the browser is 'chrome'
  if (browser != "chrome") {
    stop("Invalid browser specified. Use 'chrome'.") # Stop if it's not
  }

  # Replace forward slashes with backslashes in the download path
  download_path_temp = gsub("/", "\\\\", download_path)

  # Create a list of chrome options
  browser_options <- list(
    chromeOptions = list(
      prefs = list(
        "download.default_directory" = download_path_temp, # Set default download directory
        "download.prompt_for_download" = FALSE,           # Don't prompt for download
        "download.directory_upgrade" = TRUE,               # Upgrade download directory
        "safebrowsing.enabled" = TRUE                      # Enable safe browsing
      )
    )
  )

  # Return the browser name and options as a list
  return(list(browserName = browser, options = browser_options))
}

# Function to login to a website using Selenium
login_to_website <- function(remDr, url, username, password) {
  remDr$open() # Open the remote driver
  remDr$navigate(url) # Navigate to the specified URL

  # Define XPaths for username and password input fields
  login_user <- "//*[@id=\"frmLogin\"]/div[2]/input"
  login_passwd <- "//*[@id=\"frmLogin\"]/div[3]/input"

  # Find the username and password elements using their XPaths
  login_user_ele <- remDr$findElement("xpath", login_user)
  login_passwd_ele <- remDr$findElement("xpath", login_passwd)

  # Define the username and password
  user <- list(username)
  pass <- list(password)

  # Send the username and password to their respective elements
  login_user_ele$sendKeysToElement(user)
  login_passwd_ele$sendKeysToElement(pass)

  # Define the XPath for the login button
  login <- "//*[@id=\"login_button\"]"

  # Find the login button element using its XPath
  login_ele <- remDr$findElement("xpath", login)

  # Move the mouse to the location of the login button
  remDr$mouseMoveToLocation(webElement = login_ele)

  # Click the login button
  remDr$click()
}
```

```{=html}
<!--
Here is an example on how to use the function.
This should be a reproducible and working example
-->
```
```{r examples-download_csv_auto}
# Start selenium webdriver service
connect_to_browser(dest_dir = "C:/Users/Dell/Desktop/test")
# Download CSVs
download_csv_auto(url = Sys.getenv("url"), 
                  username = Sys.getenv("username"), 
                  password = Sys.getenv("password"),
                  csv_position = "1",
                  location = c("606","607"), 
                  date = c("2024-02-18","2024-02-19"), 
                  download_path = "C:/Users/Dell/Downloads/download_rename")
```

# download_csv_schedule

`download_csv_schedule()` is used to make download task. You can download the *Yesterday* data at certain time in every day.

```{r function-download_csv_schedule}
#' Schedule automatic downloads of CSVs
#' 
#' @description
#'
#' `download_csv_schedule()` is used to make download task.
#' 
#' @param taskname A character string with the name of the task. Defaults to the filename. Should not contain any spaces.
#' @param schedule Either one of 'ONCE', 'MONTHLY', 'WEEKLY', 'DAILY', 'HOURLY', 'MINUTE', 'ONLOGON', 'ONIDLE.
#' @param starttime A time point in HH:mm format indicating when to run the script. Defaults to within 62 seconds.
#' @param startdate A date that specifies the first date on which to run the task. Only applicable if schedule is of type 'MONTHLY', 'WEEKLY', 'DAILY', 'HOURLY', 'MINUTE'. Defaults to today in '%d/%m/%Y' format. Change to your locale format if needed.
#' @param rscript_args Character string with further arguments passed on to Rscript.
#' @param ... other parameters.
#'
#' @return CSVs in the path of save_path.
#' @export

download_csv_schedule <- function(taskname, schedule, starttime, startdate, rscript_args = NULL, ...) {
  if (missing(taskname) || !is.character(taskname) || length(taskname) != 1) {
    stop("taskname must be a single character string")
  }

  if (missing(schedule) || !is.character(schedule) || length(schedule) != 1) {
    stop("schedule must be a single character string")
  }

  if (missing(starttime) || !is.character(starttime) || length(starttime) != 1) {
    stop("starttime must be a single character string")
  }

  if (missing(startdate) || !is.character(startdate) || length(startdate) != 1) {
    stop("startdate must be a single character string")
  }

  if (missing(rscript_args) || !is.list(rscript_args)) {
    stop("rscript_args must be a list of arguments")
  }

  # Save the function to a temporary script file with a shorter path
  short_temp_path <- "C:/Temp"
  dir.create(short_temp_path, showWarnings = FALSE)
  script_file <- file.path(short_temp_path, paste0(taskname, "_", sample(letters, 1), ".R"))

  my_function <- function(...) {
    pptsdd::download_csv_auto(date = Sys.Date()-1, ...)
  }

  # Save the arguments to a configuration file
  config_file <- file.path(short_temp_path, paste0("config_", taskname, ".txt"))
  cat("arg_list <- ", capture.output(dput(rscript_args)), file = config_file)

  write_function_to_script <- function(func, file_path, config_path) {
    func_name <- deparse(substitute(func))
    lines <- capture.output(dump(func_name, stdout()))
    lines <- c(lines, sprintf("source('%s')", config_path))
    lines <- c(lines, sprintf("do.call(%s, arg_list)", func_name))

    if (!file.exists(script_file)) {
      file.create(script_file)
    }

    con <- file(script_file, "w")
    on.exit(close(con), add = TRUE)
    writeLines(lines, con)
  }

  write_function_to_script(func = my_function, file_path = script_file, config_path = config_file)

  # Schedule the task
  taskscheduleR::taskscheduler_create(taskname = taskname,
                                      rscript = script_file, 
                                      schedule = schedule,
                                      starttime = starttime,
                                      startdate = startdate,
                                      rscript_args = NULL,
                                      ...)
}
```

```{r examples-download_csv_schedule}
# Make a download task
download_csv_schedule(taskname = "ppt_csv_download",
                      schedule = "DAILY",
                      starttime = "20:00",
                      startdate = format(Sys.Date(), "%Y/%m/%d"),
                      rscript_args = list(url = Sys.getenv("url"),
                                          username = Sys.getenv("username"),
                                          password = Sys.getenv("password"),
                                          location = c("606","607"),
                                          csv_position = "1",
                                          download_path = "C:/Users/Dell/Downloads/download_temp"))
# Delete download task
taskscheduleR::taskscheduler_delete("ppt_csv_download")
# Reset selenium webdriver service
disconnect_from_browser()
```

# disconnect_from_browser

`disconnect_from_browser()` is used to reset selenium webdriver service. You can use this function after using `download_csv_auto()` and `download_csv_schedule()`.

```{r function-connect_to_browser}
#' Reset selenium webdriver service
#' 
#' @description
#'
#' `disconnect_from_browser()` is used to reset selenium webdriver service.
#'
#' @return NULL
#' 
#' @importFrom wdauto "reset_cs"
#' @export

disconnect_from_browser <- function() {
  wdauto::reset_cs()
}
```

```{r examples-disconnect_from_browser}
disconnect_from_browser()
```

# get_csv

```{r function-get_csv}
#' Direct web scraping CSVs
#' 
#' @description
#' 
#' `get_csv()` allows you to directly download CSV files from the web. You can download CSV data for a specific location range or date range. 
#'
#' @param url A character string specifying the URL to log into.
#' @param username A character string specifying the username for login.
#' @param password A character string specifying the password for login.
#' @param location_min A character string specifying the minimum location.
#' @param location_max A character string specifying the maximum location.
#' @param date_min A Date object specifying the earliest date.
#' @param date_max A Date object specifying the latest date.
#' @param download_path A character string specifying the path where the downloaded CSV file should be saved.
#' @param show_message A logical value. If TRUE, a message will be displayed after the download. Default is FALSE.
#'
#' @return CSVs in the path of download_path.
#' 
#' @export

get_csv <- function(url, username, password, location_min, location_max, date_min, date_max, download_path, show_message = FALSE) {
  login_nedap(url, username, password) |>
    download_csv(location_min, location_max, date_min, date_max, download_path, show_message)
}

is_error_response <- function(resp) {
  httr2::resp_status(resp) >= 400
}

error_message_body <- function(resp) {
  paste("Error occurred with status code:", httr2::resp_status(resp))
}

login_nedap <- function(url, username, password) {
  # check if input parameters are missing
  if (missing(url) | missing(username) | missing(password)) {
    stop("Missing required input parameter(s).")
  }

  # check input parameters
  stopifnot(is.character(url), length(url) == 1)
  stopifnot(is.character(username), length(username) == 1)
  stopifnot(is.character(password), length(password) == 1)

  # create login request
  login_request <- httr2::request(paste0(url, "/login/LoginPage.web")) |>
    httr2::req_method("post") |>
    httr2::req_body_form(select_username = username, input_password = password) |>
    httr2::req_cookie_preserve(path = tempfile())

  # perform the request and get response
  login_response <- httr2::req_perform(login_request)

  # check if login is successful
  if (httr2::resp_status(login_response) != 200) {
    stop("Failed to login, please check your username or password.")
  }

  # get the login respond
  login_respond <- login_request |>
    httr2::req_retry(max_tries = 3, is_transient = \(resp) httr2::resp_status(resp) %in% c(429, 500, 503), backoff = ~10) |>
    httr2::req_error(is_error = is_error_response, body = error_message_body) |>
    httr2::req_url(paste0(url, "/pigperformancetesting/reports/DownloadCsvDataReport.web"))

  return(login_respond)
}

download_csv <- function(login_respond, location_min, location_max, date_min, date_max, download_path, show_message) {
  # check if input parameters are missing
  if (missing(login_respond) | missing(location_min) | missing(location_max) | missing(date_min) | missing(date_max) | missing(download_path)) {
    stop("Missing required input parameter(s).")
  }

  # check input parameters
  stopifnot(is.character(location_min), length(location_min) == 1)
  stopifnot(is.character(location_max), length(location_max) == 1)
  stopifnot(is.character(date_min), length(date_min) == 1)
  stopifnot(is.character(date_max), length(date_max) == 1)
  stopifnot(is.character(download_path), length(download_path) == 1)

  # create params
  params <- list(location_min = location_min, location_max = location_max, date_min = as.character(paste0(date_min, "T00:00:00Z")), date_max = as.character(paste0(date_max, "T00:00:00Z")))

  # perform the request and get response
  login_respond <- login_respond |>
    httr2::req_url_query(generate = "1", !!!params) |>
    httr2::req_perform()

  # check if the request is successful
  if (httr2::resp_status(login_respond) != 200) {
    stop("Failed to download csv, please check your parameters.")
  }

  # get the content and write to file
  content <- httr2::resp_body_string(login_respond)
  # check if location_min and location_max, date_min and date_max are the same
  location <- if(location_min == location_max) location_min else paste(location_min, location_max, sep="_")
  date <- if(date_min == date_max) date_min else paste(date_min, date_max, sep="_")
  filename <- paste0("location", location, "_", date, "date_", Sys.Date(), "download.csv")
  writeLines(content, file.path(download_path, filename))
  if (show_message) {
    cat(crayon::blue("\u25CF"), "Locations:", location, "and Dates:", date, "downloaded\n")
  }
}
```

```{r examples-get_csv}
# Download CSV data for a specific location range or date range.
get_csv(url = Sys.getenv("url"),
        username = Sys.getenv("username"),
        password = Sys.getenv("password"),
        location_min = "406",
        location_max = "407",
        date_min = "2024-02-18",
        date_max = "2024-02-19",
        download_path = "C:/Users/Dell/Downloads/download_rename", 
        show_message = TRUE)
```

# get_csv_auto

```{r function-get_csv_auto}
#' Direct web scraping CSVs
#' 
#' @description
#' 
#' `get_csv_auto` allows you to directly download CSV files from the web. You can download CSV data for a specific location or date.
#'
#' @param url A character string specifying the URL to log into.
#' @param username A character string specifying the username for login.
#' @param password A character string specifying the password for login.
#' @param location A character string specifying the location.
#' @param date A Date object specifying the date.
#' @param download_path A character string specifying the path where the downloaded CSV file should be saved.
#' @param show_message A logical value. If TRUE, a message will be displayed after the download. Default is FALSE.
#'
#' @return CSVs in the path of download_path.
#' 
#' @importFrom cli "pb_spin" "pb_current" "pb_total"
#' @export

get_csv_auto <- function(url, username, password, location, date, download_path, show_message = FALSE){
  # Function to check and create subdirectories
  checkAndCreateSubdirs(download_path)

  # Login url
  login_request <- login_nedap(url, username, password)

  # download csv in each station each day
  download_oneday_eachstation <- function(location, date) {
    download_csv(login_respond = login_request, location_min = location, location_max = location, date_min = date, date_max = date, download_path, show_message)
  }
  all_station_perday <- function(date) {
    # check if input parameter is missing
    if (missing(date)) {
      stop("Missing required input parameter: date.")
    }

    # check input parameter
    stopifnot(length(date) == 1)

    # Convert the integer date to a Date object and format it
    date <- format(as.Date(date), "%Y-%m-%d")

    # create a data frame with all combinations of location and date
    all_comb_station <- tidyr::expand_grid(location = location, date = date)

    cat(crayon::yellow("\u25CF"), "Downloading CSVs for date:", date, "\n")

    # download the csv file for each combination of location and date
    purrr::pwalk(all_comb_station, ~download_oneday_eachstation(location = ..1, date = ..2), .progress = F)

    # Function to rename a csv file
    Rename_csv <- function(csv) {
      # Extract the name of the csv file without the extension
      csv_name <- tools::file_path_sans_ext(basename(csv))

      # Extract location and region from the csv_name using a regex pattern
      location <- stringr::str_extract(csv_name, "(?<=location)\\d+")

      # Extract download date from the csv_name using a regex pattern
      #download_date <- stringr::str_extract(csv_name, "(?<=_)\\d+-\\d+-\\d+(?=_)")

      # Determine the target folder based on the file size
      target_folder <- ifelse(file.size(csv) < 1024, "EmptyCSVs", "NonEmptyCSVs")

      # Construct the destination path
      destination_path <- file.path(download_path, target_folder, location)

      # Create the destination directory if it does not exist
      dir.create(destination_path, showWarnings = FALSE)

      # Rename the file
      file.rename(from = csv, to = file.path(destination_path, csv_name))
    }

    # Get a list of all csv files in the download directory
    down_list <- list.files(path = download_path, all.files = T, full.names = T, recursive = F, pattern = ".csv$")

    # Filter the list to keep only the files that were downloaded today
    down_list_keep <- down_list[lubridate::as_date(file.info(down_list)$mtime) == lubridate::as_date(Sys.time())]

    # Apply the rename_csv function to each file in the filtered list
    purrr::walk(down_list_keep, Rename_csv)
  }
  purrr::walk(date, all_station_perday, .progress = list(
    type = "iterator",
    format = "{cli::pb_spin} Downloading {cli::pb_current}/{cli::pb_total} dates",#"Downloading [:date] {cli::pb_bar} {cli::pb_percent}",
    clear = TRUE))
  cat(crayon::green("\u25CF"), "All stations and dates nedap ppt CSVs had been downloaded.\n")
}
```

```{r examples-get_csv_auto}
# Download CSV data for a specific location or date
get_csv_auto(url = Sys.getenv("url"),
             username = Sys.getenv("username"),
             password = Sys.getenv("password"),
             location = c("607","608"),
             date = c("2024-02-18", "2024-02-19"),
             download_path = "C:/Users/Dell/Downloads/download_rename")
```

# get_csv_schedule

```{r function-get_csv_schedule}
#' Schedule automatic downloads of CSVs
#' 
#' @description
#'
#' `get_csv_schedule()` is used to make download task.
#' 
#' @param taskname A character string with the name of the task. Defaults to the filename. Should not contain any spaces.
#' @param schedule Either one of 'ONCE', 'MONTHLY', 'WEEKLY', 'DAILY', 'HOURLY', 'MINUTE', 'ONLOGON', 'ONIDLE.
#' @param starttime A time point in HH:mm format indicating when to run the script. Defaults to within 62 seconds
#' @param startdate A date that specifies the first date on which to run the task. Only applicable if schedule is of type 'MONTHLY', 'WEEKLY', 'DAILY', 'HOURLY', 'MINUTE'. Defaults to today in '%d/%m/%Y' format. Change to your locale format if needed.
#' @param rscript_args Character string with further arguments passed on to Rscript.
#' @param ... other parameters.
#'
#' @return CSV files in the path of save_path.
#' @export

get_csv_schedule <- function (taskname, schedule, starttime, startdate, rscript_args = NULL, ...) {
  if (missing(taskname) || !is.character(taskname) || length(taskname) !=
      1) {
    stop("taskname must be a single character string")
  }
  if (missing(schedule) || !is.character(schedule) || length(schedule) !=
      1) {
    stop("schedule must be a single character string")
  }
  if (missing(starttime) || !is.character(starttime) || length(starttime) !=
      1) {
    stop("starttime must be a single character string")
  }
  if (missing(startdate) || !is.character(startdate) || length(startdate) !=
      1) {
    stop("startdate must be a single character string")
  }
  if (missing(rscript_args) || !is.list(rscript_args)) {
    stop("rscript_args must be a list of arguments")
  }
  short_temp_path <- "C:/Temp"
  dir.create(short_temp_path, showWarnings = FALSE)
  script_file <- file.path(short_temp_path, paste0(taskname,
                                                   "_", sample(letters, 1), ".R"))
  my_function <- function(...) {
    pptsdd::get_csv_auto(date = Sys.Date() - 1,
                         ...)
  }
  config_file <- file.path(short_temp_path, paste0("config_",
                                                   taskname, ".txt"))
  cat("arg_list <- ", capture.output(dput(rscript_args)), file = config_file)
  write_function_to_script <- function(func, file_path, config_path) {
    func_name <- deparse(substitute(func))
    lines <- capture.output(dump(func_name, stdout()))
    lines <- c(lines, sprintf("source('%s')", config_path))
    lines <- c(lines, sprintf("do.call(%s, arg_list)", func_name))
    if (!file.exists(script_file)) {
      file.create(script_file)
    }
    con <- file(script_file, "w")
    on.exit(close(con), add = TRUE)
    writeLines(lines, con)
  }
  write_function_to_script(func = my_function, file_path = script_file,
                           config_path = config_file)
  taskscheduleR::taskscheduler_create(taskname = taskname,
                                      rscript = script_file, schedule = schedule, starttime = starttime,
                                      startdate = startdate, rscript_args = NULL, ...)
}
```

```{r examples-get_csv_schedule}
# Make a download task
get_csv_schedule(taskname = "ppt_csv_download",
                 schedule = "DAILY",
                 starttime = "20:00",
                 startdate = format(Sys.Date(), "%Y/%m/%d"),
                 rscript_args = list(url = Sys.getenv("url"),
                                     username = Sys.getenv("username"),
                                     password = Sys.getenv("password"),
                                     location = c("606","607"),
                                     download_path = "C:/Users/Dell/Downloads/download_rename"))
# Delete download task
taskscheduleR::taskscheduler_delete("ppt_csv_download")
# Reset selenium webdriver service
disconnect_from_browser()
```


That's it ! This the end of the documented story of our package. All components are there.

```{=html}
<!-- 
# Inflate your package

You're one inflate from paper to box.
Build your package from this very Rmd using `fusen::inflate()` 
-->
```
```{r development-inflate, eval=FALSE}
fusen::inflate(flat_file = "dev/csv_download.Rmd",
               check = T, vignette_name = "Basic Usage")

#fusen::load_flat_functions(flat_file = "dev/flat_full.Rmd")

```

```{=html}
<!-- 
- Verify your `"DESCRIPTION"` file has been updated
- Verify your function is in `"R/"` directory
- Verify your test is in `"tests/testthat/"` directory
- Verify this Rmd appears in `"vignettes/"` directory 
-->
```
