---
title: "flat_full.Rmd for working package"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{=html}
<!-- 
Run this 'development' chunk

Store every call to library() that you need to run chunks line by line, as in a classical Rmd for analysis
-->
```
```{r development, include=FALSE}
library(testthat)
library(purrr)
library(RSelenium)
library(taskscheduleR)
```

```{=html}
<!--
# Description of your package

This will fill the description of your package.
Fill and run the content of this chunk, before anything else. 

Note: when you will use other flat templates, this part will be in a separate file. Do not be surprised!
-->
```
```{r description, eval=FALSE}
# Describe your package
fusen::fill_description(
  pkg = here::here(),
  fields = list(
    Title = "Breeding Tools",
    Description = "An R package that can automatically or periodically download data from the Nedap website in pig farm.",
    `Authors@R` = c(
      person("Guo Meng", email = "tony2015116@163.com", role = c("aut", "cre")),
      person(given = "Guo Meng", role = "cph")
    )
  ),
  overwrite=T
)
# Define License with use_*_license()
usethis::use_mit_license("Guo Meng")
#usethis::use_ccby_license()
```

# download_csv_auto

This is the first function of our package. You can free up you hands and download pig performance test station data using function `download_csv_auto()`.

```{=html}
<!-- 
This first section shows:

- the three parts necessary for a package: 'function', 'examples' and 'tests'.  
  + Note that the three following chunks have names accordingly.

-->
```
```{r function-download_csv_auto}
#' Automatically download CSV
#' 
#' @description
#'
#' `download_csv_auto()` is deprecated. We will soon be totally
#' 
#' @param url The url of pig performance test station website
#' @param username The username of pig performance test station website
#' @param password The password of pig performance test station website
#' @param csv_position The pisiton of csv download item
#' @param location Numeric value in string format
#' @param data_date The dates of data download
#' @param download_path The folder of downloading csv files
#' @param save_path The folder you need to save renamed csv files
#' @param ... other parameters
#'
#' @return CSV files in the path of save_path
#' @export

download_csv_auto <-
  function (url,
            username,
            password,
            csv_position,
            location,
            data_date,
            download_path,
            save_path,
            ...) {
    # Argument checks
    if (!is.character(url))
      stop("url must be a character string")
    if (!is.character(username))
      stop("username must be a character string")
    if (!is.character(password))
      stop("password must be a character string")
    if (!is.character(csv_position))
      stop("csv_position must be a character value")
    if (!is.vector(location) ||
        !is.character(location))
      stop("location must be a character vector")
    if (is.null(try(as.Date(download_date), silent = TRUE)
    ))
      stop("The 'download_date' parameter must be a valid date string.")
    if (!is.character(download_path))
      stop("download_path must be a character string")
    if (!is.character(save_path))
      stop("save_path must be a character string")

    download_path_temp = gsub("/", "\\\\", download_path)
    chrome_options <- list(chromeOptions = list(
      prefs = list(
        "download.default_directory" = download_path_temp,
        "download.prompt_for_download" = FALSE,
        "download.directory_upgrade" = TRUE,
        "safebrowsing.enabled" = TRUE
      )
    ))

    remDr <- RSelenium::remoteDriver(
      browserName = "chrome",
      extraCapabilities = chrome_options,
      remoteServerAddr = "127.0.0.1",
      port = 4444
    )


    suppress_print <- function() {
      remDr$open()
      remDr$navigate(url)
      login_user <- "//*[@id=\"frmLogin\"]/div[2]/input"
      login_passwd <- "//*[@id=\"frmLogin\"]/div[3]/input"
      login_user_ele <- remDr$findElement("xpath", login_user)
      login_passwd_ele <- remDr$findElement("xpath", login_passwd)
      user <- list(username)
      pass <- list(password)
      login_user_ele$sendKeysToElement(user)
      login_passwd_ele$sendKeysToElement(pass)
      login <- "//*[@id=\"login_button\"]"
      login_ele <- remDr$findElement("xpath", login)
      remDr$mouseMoveToLocation(webElement = login_ele)
      remDr$click()
    }

    capture.output(suppress_print())

    dir.create(paste0(here::here(save_path, "have_data")), showWarnings = FALSE)
    dir.create(paste0(here::here(save_path, "no_data")), showWarnings = FALSE)

    Sys.sleep(sample(10, 1))
    iter_download <- function(station, data_date, ...) {
      choose_item <- "/html/body/div[1]/div[1]/ul/li[4]/a"
      choose_ele <- remDr$findElement("xpath", choose_item)
      remDr$mouseMoveToLocation(webElement = choose_ele)
      remDr$click()
      download_item <-
        paste0("//*[@id=\"reports_page\"]/div[2]/div/div[3]/ol/li[",
               {
                 {
                   csv_position
                 }
               },
               "]/a")
      download_ele <- remDr$findElement("xpath", download_item)
      remDr$mouseMoveToLocation(webElement = download_ele)
      remDr$click()
      location_start <-
        "//*[@id=\"criteria\"]/report-selection-range/div/div/div/div[1]/input"
      location_end <-
        "//*[@id=\"criteria\"]/report-selection-range/div/div/div/div[2]/input"
      location_ele_start <- remDr$findElement("xpath",
                                              location_start)
      location_ele_end <- remDr$findElement("xpath",
                                            location_end)
      location_ele_start$clearElement()
      location_ele_end$clearElement()
      location_start_num <- list(station, key = "enter")
      location_ele_start$sendKeysToElement(location_start_num)
      location_ele_end$clickElement()
      date_start <- "//*[@id=\"datetimepicker0\"]/input"
      date_end <- "//*[@id=\"datetimepicker1\"]/input"
      date_ele_start <- remDr$findElement("xpath", date_start)
      date_ele_end <- remDr$findElement("xpath", date_end)
      date_ele_start$clearElement()
      date_need_to_download <-
        stringr::str_replace_all(as.character(data_date),
                                 "-", ".")
      date_start_num <- list(date_need_to_download, key = "enter")
      date_end_num <- list(date_need_to_download, key = "enter")
      date_ele_start$sendKeysToElement(date_start_num)
      date_ele_end$clearElement()
      date_ele_end$sendKeysToElement(date_end_num)
      download_button <-
        "//*[@id=\"reports_download_csv_data\"]/div[4]/button"
      download_button_ele <- remDr$findElement("xpath",
                                               download_button)
      remDr$mouseMoveToLocation(webElement = download_button_ele)
      remDr$click()
      remDr$refresh()
      #dir.create(paste0(here::here({{save_path}},{{station}})), showWarnings = FALSE)
    }

    Sys.sleep(3)

    # all_comb <- purrr::cross2(location, data_date) #注释的两行就可以完整的下载所有日期和所有测定站的csv数据
    # purrr::walk(all_comb, ~iter_download(.x[[1]], .x[[2]]), ...)

    all_station_oneday <-
      function(oneday_date, ...) {
        # Convert the integer date to a Date object and format it
        formatted_date <-
          format(as.Date(oneday_date, origin = "1970-01-01"), "%Y-%m-%d")

        cat("Downloading csv for date:", formatted_date, "\n")


        # # Create a progress bar for each date
        # pb <- txtProgressBar(
        #   min = 0,
        #   max = length(location),
        #   style = 1
        # )
        #
        # purrr::walk(location, function(station, ...) {
        #   iter_download(station, oneday_date, ...)
        #
        #   # Update the progress bar
        #   setTxtProgressBar(pb, which(location == station))
        # }, ...)
        #
        # # Close the progress bar
        # close(pb)

        #为了方便修改csv名称包含数据日期，以某一天日期为参数，写函数all_station_oneday()下载该天所有测定站csv数据
        all_comb_station <-
          purrr::cross2(location, oneday_date) #组合所有测定站和单个日期
        purrr::walk(all_comb_station, ~ iter_download(.x[[1]], .x[[2]]), ...)#下载该日期所有csv数据


        rename_csv <- function(csv, ...) {
          #写函数rename_csv()来改变csv的名称
          csv_name <- tools::file_path_sans_ext(basename(csv))
          location_region <-
            stringr::str_extract(csv_name, "(?<=_)[:lower:]+\\d+-\\d+(?=_)")
          download_date <-
            stringr::str_extract(csv_name, "(?<=_)\\d+-\\d+-\\d+(?=_)")
          #download_date_trans <- stringr::str_replace_all(as.character(download_date), "-", ".")
          csv_new_name <-
            paste0(
              location_region,
              "_",
              oneday_date,
              "data",
              "_",
              download_date,
              "download",
              ".csv"
            )
          ifelse(
            file.size(csv) < 1024,
            dir.create(
              paste0(here::here(save_path, "no_data"), "/", location_region),
              showWarnings = FALSE
            ),
            dir.create(
              paste0(
                here::here(save_path, "have_data"),
                "/",
                location_region
              ),
              showWarnings = FALSE
            )
          )
          ifelse(
            file.size(csv) < 1024,
            file.rename(
              csv,
              paste0(
                here::here(save_path, "no_data"),
                "/",
                location_region,
                "/",
                csv_new_name
              )
            ),
            file.rename(
              from = csv,
              to = paste0(
                here::here(save_path, "have_data"),
                "/",
                location_region,
                "/",
                csv_new_name
              )
            )
          )

        }

        down_list <-
          list.files(
            path = download_path,
            all.files = T,
            full.names = T,
            recursive = F,
            pattern = ".csv$"
          ) #下载的csv数据列表
        down_list_keep <-
          down_list[lubridate::as_date(file.info(down_list)$mtime) == lubridate::as_date(Sys.time())] #过滤csv文件，仅保留今日下载的csv
        purrr::walk(down_list_keep, rename_csv, ...) #批量改名

      }

    purrr::walk(data_date, all_station_oneday, .progress = T, ...) #循环每个日期下载csv

    remDr$quit() #退出浏览器

    return(invisible(NULL))
  }
```

```{=html}
<!--
Here is an example on how to use the function.
This should be a reproducible and working example
-->
```
```{r examples-download_csv_auto}
stations = c("1801","1802")
data_date = c("2023-03-29","2023-03-30")
download_path = "C:/Users/Dell/Downloads/"
save_path = "C:/Users/Dell/Downloads/test/"

download_csv_auto(url = Sys.getenv("web_url"), 
                  username = Sys.getenv("user_name"), 
                  password = Sys.getenv("user_password"),
                  csv_position = "1",
                  location = stations, 
                  data_date = data_date, 
                  download_path = download_path,
                  save_path = save_path)
```

# download_csv_schedule

This is the first function of our package. You can free up you hands and download pig performance test station data using function `download_csv_schedule()`.

```{r function-download_csv_schedule}
#' Schedule automatic downloads of CSV
#' 
#' @description
#'
#' `download_csv_schedule()` is deprecated. We will soon be totally
#' 
#' @param taskname A character string with the name of the task. Defaults to the filename. Should not contain any spaces
#' @param data_date Set `Sys.Date()-1` as default data date
#' @param schedule Either one of 'ONCE', 'MONTHLY', 'WEEKLY', 'DAILY', 'HOURLY', 'MINUTE', 'ONLOGON', 'ONIDLE
#' @param starttime A timepoint in HH:mm format indicating when to run the script. Defaults to within 62 seconds
#' @param startdate A date that specifies the first date on which to run the task. Only applicable if schedule is of type 'MONTHLY', 'WEEKLY', 'DAILY', 'HOURLY', 'MINUTE'. Defaults to today in '%d/%m/%Y' format. Change to your locale format if needed
#' @param rscript_args Character string with further arguments passed on to Rscript
#' @param ... other parameters
#'
#' @return CSV files in the path of save_path
#' @export

download_csv_schedule <- function(taskname, data_date = Sys.Date()-1, schedule, starttime, startdate, rscript_args = NULL, ...) {
  if (missing(taskname) || !is.character(taskname) || length(taskname) != 1) {
    stop("taskname must be a single character string")
  }

  if (missing(schedule) || !is.character(schedule) || length(schedule) != 1) {
    stop("schedule must be a single character string")
  }

  if (missing(starttime) || !is.character(starttime) || length(starttime) != 1) {
    stop("starttime must be a single character string")
  }

  if (missing(startdate) || !is.character(startdate) || length(startdate) != 1) {
    stop("startdate must be a single character string")
  }

  if (missing(rscript_args) || !is.list(rscript_args)) {
    stop("rscript_args must be a list of arguments")
  }

  # Save the function to a temporary script file with a shorter path
  short_temp_path <- "C:/Temp"
  dir.create(short_temp_path, showWarnings = FALSE)
  script_file <- file.path(short_temp_path, paste0(taskname, "_", sample(letters, 1), ".R"))

  my_function <- function(...) {
    pptsdd::download_csv_auto(data_date = data_date, ...)
  }

  # Save the arguments to a configuration file
  config_file <- file.path(short_temp_path, paste0("config_", taskname, ".txt"))
  cat("arg_list <- ", capture.output(dput(rscript_args)), file = config_file)

  write_function_to_script <- function(func, file_path, config_path) {
    func_name <- deparse(substitute(func))
    lines <- capture.output(dump(func_name, stdout()))
    lines <- c(lines, sprintf("source('%s')", config_path))
    lines <- c(lines, sprintf("do.call(%s, arg_list)", func_name))

    if (!file.exists(script_file)) {
      file.create(script_file)
    }

    con <- file(script_file, "w")
    on.exit(close(con), add = TRUE)
    writeLines(lines, con)
  }

  write_function_to_script(func = my_function, file_path = script_file, config_path = config_file)

  # Schedule the task
  taskscheduleR::taskscheduler_create(taskname = taskname,
                                      rscript = script_file, 
                                      schedule = schedule,
                                      starttime = starttime,
                                      startdate = startdate,
                                      rscript_args = NULL,
                                      ...)
}
```

```{r examples-download_csv_schedule}
download_csv_schedule(taskname = "ppt_csv_download",
                      schedule = "DAILY",
                      starttime = "20:05",
                      startdate = format(Sys.Date(), "%Y/%m/%d"),
                      rscript_args = list(url = Sys.getenv("web_url"),
                                          username = Sys.getenv("user_name"),
                                          password = Sys.getenv("user_password"),
                                          location = c("1801","1802"),
                                          csv_position = "1",
                                          download_path = "C:/Users/Dell/Downloads",
                                          save_path = "C:/Users/Dell/Downloads/test"))
```

That's it ! This the end of the documented story of our package. All components are there.

```{=html}
<!-- 
# Inflate your package

You're one inflate from paper to box.
Build your package from this very Rmd using `fusen::inflate()` 
-->
```
```{r development-inflate, eval=FALSE}
fusen::inflate(flat_file = "dev/flat_full.Rmd",
               check = F)

#fusen::load_flat_functions(flat_file = "dev/flat_full.Rmd")

```

```{=html}
<!-- 
- Verify your `"DESCRIPTION"` file has been updated
- Verify your function is in `"R/"` directory
- Verify your test is in `"tests/testthat/"` directory
- Verify this Rmd appears in `"vignettes/"` directory 
-->
```
